\subsection{Archetype System}
The Archetype system allows both the game master and the players to easily
scale between small and large unit sizes as well as vehicles and monsters using
the same rules framework. It allows this through the use of 3 properties: body,
mind, and Spirit.  Each property is described by an integer values on the closed
interval from 0 to 4.  The sum of these integers is referred to as the power
level.  These properties provided basic features of the characters.
\subsubsection{Body}
Body affects how and what kinds of equipment may be used by the character.
There are 3 sub types of equipment: Hand, Armor, and Gear.  By default a
character may use 1 hand item and 1 Armor item;  they cannot use a gear by
default.  For each level that the character gains in body, they may increase the
carry limit of hand, armor, or gear by one level.  Heros cannot take
independent actions if they have a gear.
\subsubsection{Mind}
Mind affects the number of skills that the character may have and the initial
number of skill points that the player may have.  By default, a character has a
limit of 2 skills and a starting skill points of 1 point.  For each level that
the player gains in mind, the character gains 1 to the skill limit and +3
initial skill points.
\subsubsection{Spirit}
Spirit affects the fundamental attributes of the character.  By default, the player
has a cap of 10 attribute points and 2 attribute points.  For each level that
player gains in mind, the player gains +10 to the cap of attribute points and +2
initial attribute points.
\subsubsection{Squads}
Any group of 3 units can form a squad.  Forming the squad makes the 3 distinct
units into a single unit with a power level of +1 from the highest power level
of the units in the squad.  This is capped at no more than 3 more that the power
level of the lowest  power level in the squad.  Squads can form squads with
other squads and units can form squads with squads.  The +1 power level can be
added to Body, Mind, or Spirit provided the property does not exceed 4.  A solo
unit may not exceed a power level of 9.
\subsubsection{Some suggestions}
The power level that the GM chooses should be based off the kind of game that
the players desire.  For RPG's choose a power level of 9 with a 3/3/3 split
between body, mind, and Spirit. Tactical combat should use players with power
levels of 0 or 1.
