\documentclass[10pt, twoside]{book}
\title{Etinia}
\author{Robert Underwood}
\date{}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{makeidx}
\usepackage[paperwidth=6in,paperheight=9in,top=1in,left=0.66in,right=0.66in,textheight=6.8in,bindingoffset=5mm,twoside]{geometry}
\usepackage[table]{xcolor}
\usepackage{tabularx}



\newcommand{\skill}[7]{ 
 \noindent
 \subsection{#1}
 \rowcolors{1}{white}{white}
 \begin{tabularx}{\textwidth}{l X}
 \textbf{Level 1:}& #2 \\
 \textbf{Level 2:}& #3 \\
 \textbf{Level 3:}& #4 \\
 \textbf{Level 4:}& #5 \\
 \textbf{Level 5:}& #6 \\
 \textbf{Level $\Omega$:}& #7 \\
 \end{tabularx}
 \ignorespacesafterend
}
\newcommand{\kskill}[9]{ 
 \noindent
 \subsection{#1}
 \rowcolors{1}{white}{white}
 \begin{tabularx}{\textwidth}{l X}
 \textbf{Level 1:}& #2 \\
 \textbf{Level 2:}& #3 \\
 \textbf{Level 3:}& #4 \\
 \textbf{Level 4:}& #5 \\
 \textbf{Level 5:}& #6 \\
 \textbf{Level Further:}& #7 \\
 \textbf{Level Greater:}& #8 \\
 \textbf{Level $\Omega$:}& #9 \\
 \end{tabularx}
 \ignorespacesafterend
}
\makeindex

\begin{document}
\frontmatter
\maketitle
\tableofcontents

\mainmatter
\chapter{The Basics}
\section{WHAT IS ETINIA?}
Etinia is a game engine.  It is designed to be a toolset to facilitate a large variety of different kinds of games including Role Playing Games and Tactical Combat Games.  This book contains the core rules for using this system,some character samples,and the details of a world system designed to work with the Etinia engine.
\section{A NOTE ON ROLEPLAYING}
The objective of a roleplaying game is to collaboratively tell a story between the players.  For some players, this is best accomplished with heavy rule sets that clearly delineate skills so that each player is strictly balanced with every other player.  For others, this is best accomplished with light rule sets that allow players to do wild and crazy things that are not at all balanced.  This rule set attempts to strike the best of both worlds by creating a modular rule set.  This means the tactical players have their strict rules set, but roleplaying players may simply play without them.  Unfortunately, one of these styles requires much more precise language in order to achieve clarity.  Therefore, these rules will be written primarily to the audience of tactical players.  For those of you who prefer a lighter game, simply take the rules and focus on what kind of abilities each level provides.  For example, a Life mage who can make a fireball could also light a candle with magic.  The rules may not clearly delineate this ability but it is obvious from the spirit of the rules.  This ambiguity then requires some sort of authority.  Any ambiguity is to be determined solely by the game master.  Furthermore, these rules make several clear references to distances, for a lighter game consider anything with in 1 space to be close, 2 spaces to be mid ranged, and 3+ spaces to long ranged.  Therefore these distance rings could be used instead of a battle map.  Furthermore,for references to width assume that each weapon can hit the number of enemies equal to the area in spaces of that it could hit on a battle map.  One final recommendation for roleplaying heavy groups would be for the game master to assign a number of rp points to each player.  These points could be used to overrule a judgment call on a rule or to "re-roll" a failed attack or test.

\section{HOW TO GET STARTED}

\subsection{HERO}
The basis of Etinia is the \index{Hero}Hero.  To begin the game,one should create a Hero.  To create a Hero,one receives 11 skill points and 6 equipment points.  The skill points are used to purchase skills.  The equipment points are used to purchase equipment.  Heroes have Attributes, Skills, Abilities, Equipment, and an Elemental Affiliation.
	Attributes are basic statistics that determine how the character functions at a very basic level.  There are 4 basic attributes: Will,Strength,Defense,and Speed.  Will is the ability of the character to remain conscious after taking damage.  It determines how many hits a player may take before falling unconscious.  Will starts at 6 and may be as high as 11.  Strength is the ability of the Hero to perform actions.  It is a factor in every action.  Defense is the ability of a Hero to avoid being hit and taking damage.  It is a factor used in stopping actions done against the player.  Speed is the ability of the Hero to move quickly.  It determines when and how often Heroes move.  Strength,Defense,and Speed start at 0 and may become as high as 5.
      Skills are the ways heroes use their attributes perform actions in the game,and how heroes can improve their attributes.  Heroes can have up to 5 skills.  Skills come in 5 skill levels.  Each level is more powerful than the last and includes the abilities of every previous level.   Level 1 skills are the weakest,and level 5 skills are the most powerful.    Over the course of the game,heroes will level up.  When Heroes level up,they may acquire new skills and improve their current ones.  However,Heroes cannot have two skills with the same name.  For example,a hero cannot have Close Combat 2 and Close Combat 3.  All skills have a price in skill points based on their level.  


\begin{center}
\rowcolors{1}{white}{gray}
\begin{tabularx}{\textwidth}{X X}
\hline
Skill Level & Cost in Skill Points \\ \hline
1 & 1 \\
2 & 3 \\
3 & 6 \\
4 & 10 \\
5 & 15 \\
\hline
\end{tabularx}
\end{center}

For example,if a player wanted Battle Knowledge 3 and Cast 2 (two different skills); the player would need 8 skill points.  Skills are organized into Skill Trees based on function.  There are seven different skill trees: Attack,Defense,Knowledge,Magic,Mechanics,Ancients and Racial.  
      Skills in the Attack Tree allow characters to deal damage to opponents.  These skills are handy for any damage dealing character or weapons master character.  Improving the skills allows you to increase the range,deal more hits,and unlock more options.
      The Defense Tree allows player to reduce both directly and indirectly the damage that they receive.  These skills are useful for any wall or tank character.  As characters level up these skills,they will be able to greater reduce the damage they take.
      The Knowledge Tree is the house of all knowledge in the game.  The uses of the skills in the knowledge tree are as diverse as the knowledge itself.  Each skill contains a variety of different abilities that become more and more potent as the character advances them.
      The Magic Tree is home to all things dealing with magic.  Characters based off mages,sages,and other magic casters will benefit greatly from the skills in this tree.  However with great power comes great cost.  Many skills in this tree require energy to be expended to be used.  As the skills in this tree are advanced,the abilities become more and more powerful.
      The Mechanics Tree is where robots programs and machines take their power.  However,with great power comes great cost.  Many skills in this tree can be prevented when damage is taken.  As the skills in this tree are advanced,the abilities become more and more powerful.
      The Ancients Tree is home to old power.  Heroes based off colossal warriors can find their skills here.  These skills give extreme power for a limited time.  As the skills in this tree are advanced,the abilities become more and more powerful.
      The Racial Tree contains skills that change the attributes of the heroes who have them.  Skills such as Strength,Defense,Speed,and Will are located here as well as special racial abilities.  As these skills are advanced,the attributes that they represent are improved.
	The skills that a Hero has determine which Abilities they may use.  Abilities are specific actions that a player may perform.  For example a character with Close Combat 1 gains the ability long cut which when equipped with a short range weapon may target any hero in within two panels in front of him.  In addition having the necessary skill,Heroes must also choose to ready a skill.  Readying a skill is simply including the ability in a list of skills that the hero will use.  Abilities may be readied at any time outside of combat.  Each hero may have up to 20 abilities readied.

\subsection{EQUIPMENT}
\subsubsection{Making Equipment}
Heroes also get 5 Equipment Points to use to purchase equipment.  There are several different types of equipment.\\
\rowcolors{2}{white}{gray}
\begin{tabularx}{\textwidth}{X X}
\hline
Equipment Type & Function \\
\hline 
Armor & Protects Hero;  Sets affinity\\
Helm & Protects Hero\\
Footwear & Protects Hero\\ 
Short Range & Use Close Combat attacks\\
Long Range & Use Long Range attacks \\
Staff & Improves Magic Tree attacks\\
Shield & Use Shield abilities\\
Gloves & Improves Melee attacks\\
\hline
\end{tabularx}\\

All equipment is made using the following materials which determine its statistics
\begin{center}
\rowcolors{2}{white}{gray}
\begin{tabularx}{\textwidth}{X X X X}
\hline
Cost& Material& Attack/Defense & Engineer\\
\hline
1 & Organic & 1/1 & 0\\
3& Stone & 2/2 & 0\\
6& Ore& 3/3& 1\\
10& Metal& 4/4& 2\\
15& Processenium& 5/5& 3\\
N/A& Refined Alloy& 6/6& 3\\
N/A& Legendary Alloy& 7/7& 4\\
\hline
\end{tabularx}\\
\end{center}


\subsubsection{IMPORVING EQUIPMENT}

\paragraph{ENGINEERING}

Engineering is preformed by the Technical skill.  Each material has different properties that affect the extent to which it can be modified by engineered.  There is no cost to engineering an item during character creation.  The effects of the modifications are permanent.  Equipment may only be engineered at creation.\\
\begin{center}
\rowcolors{1}{white}{gray}
\begin{tabularx}{\textwidth}{X X}
\hline
ENGINEERING LEVEL & EFFECT \\

\hline0 & No effect \\
1 & $+1$ attack $-1$ defense or $+1$ defense $-1$ speed or $+1$ speed $-1$ attack \\
2 & 2 Rank 1 or +1 MP \\
3 & 2 Rank 2 or Gain Ability from a Skill Level 1\\
4 & 2 Rank 3 or Gain Level 1 Skill \\
\hline
\end{tabularx}\\
\end{center}

\paragraph{ALCHEMY}
Alchemy is preformed by the alchemy skill.  All materials may use all levels of alchemy.  The effects of alchemy are permanent.  Characters with the alchemy skill do not have to pay the cost to use alchemy on their weapons
\begin{center}
\rowcolors{2}{white}{gray}
\begin{tabularx}{\textwidth}{X X}
\hline 
Cost in equipment points &Effect\\
\hline 1 & Add element\\
3 & Add Ability from a Skill\\
6 & Add a level 1 skill \\
\hline
\end{tabularx}
\end{center}

\paragraph{ADVANCED WEAPONS}
Advancements may be purchased for any weapon.  There are 6 types of advancements.  Advancements costs 15 points.  Each weapon may have 3 advancements.  The advancements may be of the same type,different types,or any combination thereof.  The advancements do not affect the elemental affinity of a weapon.

\begin{center}
\rowcolors{1}{white}{gray}
\begin{tabularx}{\textwidth}{X X}
\hline
Advancement & Effect\\
\hline
Earth & $+5$ to the attack stat\\
Sky & $+3$ to all initiative draws \\
Justice & $+1$ lv to all skills equipped to this weapon\\
Sea & Weapon gains and additional type attribute (short/long/melee/defense) or a second elemental affinity \\
Life & Gives the user $+1$ Will\\
Abandon & $+ 1$ to the card bonus ($card\,\geq15$ then the card is treated as a joker) \\
\hline
\end{tabularx}
\end{center}

\subsubsection{HERO DEFINITION}

All Player Characters and most computer controlled characters are Heroes.  Heroes have the following characteristics:
Attributes: There are 4 attributes: Strength,Speed,Defense,and Will.Strength,Speed,and Defense have a maximum value of 5,and Will has a maximum value of 11.Strength,Speed,and Defense start at 0 and Will starts at 6.
Skills: a list of 5 skills that determine what abilities may be placed in the abilities list.
Abilities: a list of all possible actions that may be chosen from in a given battle.
Equipment: there are 5 equipment slots: Helm,Chest,Foot,and 2 hands.  See the section on equipment for more detail.
Elemental Affiliation: the element affiliated with a character.  Element is determined by the element of the hero‚Äôs armor.
Info: non-essential information such as name,description,etc.
\subsubsection{EQUIPMENT Definition}

Weapons have the following characteristics:
Attack: how much damage a weapon can do
Defense: how much damage a weapon can stop
Location: where the weapon is equipped: helm,foot,chest,hand,dual hand
Elemental Affiliation: what elemental type of damage a weapon does
Abilities: a specific ability that may be used.
Skills: Two slots for skills.  One slot may be accessed by engineering (Knowledge Tree: Technical Skill) the other by enchanting (Magic Tree: Alchemy Skill).  Weapons may also be purchased
/ acquired with skills in these slots.  Treat Skills equipped in this way a 
+1 level for the specific skill.
\subsection{STATUS SYSTEM}
Status effects modify the attributes of a character.  There are seven types of status effects.  
\begin{itemize}
\itemÄ	Buffs and Debuffs increase or decrease a statistic for a given duration.  
\item Recurring Buffs and Debuff do the same except the increase/
decrease is applied each round.
\item Add ability grants the use of a specific ability.
\item Remove ability prevents a specific ability or class of abilities.
\item Remove Equipment ‚Äì prevents the use of a piece of equipment until the duration has expired.
\item Prevent Status ‚Äì prevents the assignment of certain types of status effects
\item If Then Status- When an allowed if then occurs then a status is imparted
\end{itemize}
\chapter{SKILLS}
%\begin{multicols}{2}
\section{BASIC ABILITIES}
\textbf{Basic Melee Attack :} use strength as weapon; -5 modifier\\
\textbf{Basic Weapon Attack :} range 1; -8 modifier \\
\textbf{Basic Long Range Attack :} range 2 not 1; -8 modifier\\
\textbf{Basic Defense :} use defense as specific skill; -5 modifier\\
\textbf{Move: } move 1 space\\
\textbf{Revival:}  Heroes with 0 will may on a 50\% chance revive to 1 will

\section{ATTACK TREE}
\skill{CLOSE COMBAT}{Long Cut and Wide Cut}{Spin Cut}{Stab (sword inflict bleeding) and Life cut}{Shock Wave}{Wide Wave and Great Spin}{Storm of Blades (Spin Cut inflict bleeding)}

\skill{LONG RANGE}{Bow shot (target a line; hit nearest object; range 5 squares orthogonal) and Arc Shot (target one tile up to 3 spaces away from user)}{V shot and wide shot and Shotgun Spread (triangle of height 2)}{Focus (Status; Duration 2; increase range of long range by 2)}{Spreader Shot}{Barrage 2 (fire two shots; -5 modifier to both shots)}{Use two abilities from this tree in one move at -8 modifier each}
\textit{Long Range cannot target adjacent objects}

\skill{MELEE}{Punch (short sword + knockback) and Kick (wide)}{Grab - pulls a player from unto 2 panels away to player}{(Throws may be used in the same action as grab) Far throw (knockback 2) and High Throw (paralyze)Down Throw(damage)}{ Combo Strike(2 abilities from melee)+3 knock back for far throw}{Combo Strike (3 abilities from melee,-5 to hit for each attack in chain)}{passive ends the turn immediately when this player is attacked even if during a chain attack}

\skill{OVERDRIVE}{Berserk Mode +5 modifiers for 3 turns; then,take 1 damage}{deal a Critical Hit for Two J+ in addition to a joker}{All attacks are Critical Hits when the hero is at 1hp}{Finisher (do 2 damage to foes with Debuffs)}{Super Mode- charge for 1 turn then +5 modifier for 3 turns}{Charge for 7 turns; Activate Final Form (boost all skills to lv 5; gain all $\Omega$s; max attributes; if damage $>1$,damage $-1$)}

\skill{ATTACK IMPROVISATION}{Close Combat to Long Range and Long Range to Close Combat}{Close Combat to Defense and Long Range to Defense}{Defense to Close Combat}{Defense to Long Range}{Dual Handed ‚Äì use two weapons while attacking}{Melee to Long Range,Melee to Close Combat,Melee to Defense}

\skill{DEXTERITY}{Aim- draw an extra card and choose highest}{Aim to Status Shot (3 turns buff/ Debuff)}{$+1$ hand (passive)}{Aim to Power Shot (2 damage)}{Aim to Trick Shot ‚Äì do a close combat attack after arc shot}{On Joker ignore armor}

\skill{Light Combat}{"Quick Attack" +1 initiative next turn}{move and attack}{"Stab" inflict bleeding}{"Throw Knife" allows long range attack}{ignore abilities of targets allies during this attack}{Unit may attack an adjacent foe once per round as a free action}

\section{DEFENSE TREE}
\skill{SHIELD}{ Block ‚Äì protects user}{Block‚Äì protects user (passive)}{Cover Ally ‚Äì protects targeted adjacent ally with shield}{Cover Allies ‚Äì Protects all adjacent allies}{Cover all ‚Äì Protects all adjacent allies (passive; optional; pre-flex)}{Replace all references in shield to "adjacent" with up to 2 spaces away}

\skill{COUNTER}{Status Counter if less for close combat}{Status Counter if less for long range}{Status Counter if less for energy or defense}{Status Counter with "if then" instead of less}{Status Counter with if more instead of less}{Counters 2 actions instead of 1}

\skill{TRAP}{Lay Trap that inflicts status}{Lay Trap that does damage to target}{Lay trap that hits target and adjacent for damage}{Lay trap that hits target and adjacent for Status}{Lay trap to convert neutral unit}{Throw trap up to 3 panels away}\\
\textit{Traps activate during the status phase of the turn}

\skill{STEALTH}{Avoid Sight ‚Äì can be seen only when adjacent until action (Status duration 3)}{Surprise ‚Äì Do max flank when coming out of stealth}{Avoid Sight 2 - cannot be seen until action taken (Status duration 3)}{Steal: Take a non-equipped item from target when coming out of stealth}{When hidden,Inflict bleeding on attack}{Reflex ‚Äì when hidden,draw to avoid hit}

\skill{DISARM}{Remove Traps}{Remove Equipment}{prevent all target hero‚Äôs actions for1 round}{Remove Weapons}{prevent all target hero's actions for 3 rounds}{Remove all equipment except weapons}

\skill{PERCEPTION}{See Skills}{See Traps}{See Abilities}{See Stealth (stealth status -1)}{See Intent (pre-flex once per battle)}{Eagle Vision:  Stealth -2,Prevent Pre-flex,Pre-flex twice}

\skill{AURA}{Create a single use defensive Aura of 2lv/2lv}{Create a single use short weapon Aura of 2lv/2lv}{Create a single use long weapon Aura of 2lv/2lv}{Change aura elemental affinity (effects items made of aura)}{Charge Aura ‚Äì durability of aura weapons $+1$ use per charge}{Charging aura also gains $+1/+1$ to aura strengths (cap 5)}

\section{KNOWLEDGE}

\skill{GENERAL}{+1 to any knowledge tree skill (only one at a time)}{Cook Food}{Unlock Further Knowledge}{Sing: ranged area effect buff/Debuff}{Unlock Great Knowledge}{Insight ‚Äì target a foe at beginning of battle; all attacks by this hero deal +1 damage to that foe}

\kskill{BATTLE}{Pilot Vehicles/Creatures}{Quick Mount Dismount}{Form Squad,Disband Squad,Pilot and Turret at same time}{Supply Drop
}{Forces Drop}{Formation Moves}{+3 Forces Cap (Limit 2 units may use this per side)}{None}

\kskill{MAGIC}{"Throw" Verb; "Bolt" noun; 1 elemental adjective}{2nd elemental adjective; "Block" noun; "Place" Verb}{3rd Elemental Adjective; All Verbs}{4th Elemental Adjectives; All Nouns}{Stop Any Magic}{All Adverbs}{Stop Magic and counter with same spell without cost}{None}


\kskill{HISTORIC}{Identify Skills of Foes}{Multilingual,Basic Map w/o fog of war}{Identify abilities and equipment of foes}{Map with Positions of all characters}{Ancient Languages,Path finding: add 1 feature to map before battle}{Map updates}{terraforming: add 2 features to map before battle}{None}

\kskill{TECHNICAL}{Craft with material levels 1 and 2}{Technical Abilities lv1}{Craft with material levels 3 and 4}{Technical Abilities lv2,Research}{Craft with materials level 5+}{Level Further: Engineering lv1 and lv2 }{Engineering lv3 and lv 4}{None}

\kskill{NATURALISTIC}{Acquire item on KO 10\%,Farm Plants}{Convert Neutral Creatures}{Acquire item on KO 20\%,Farm Animals for food}{Order One Creature}{Acquire item on KO 30\%,Farm Animals for Allies}{Order Three Creatures}{Acquire item on KO 50\%}{None}

\kskill{MEDICAL}{First Aid: heal 1 hp}{Clear One Status}{Surgery (Heal 3hp or Clear All status with 2 turn recharge)}{Pharmacology (2 turn buff/debuff including HP)}{Improved Pharmacology (4 turn buff/debuff including HP)}{Immunizations (prevent Debuff of a given type)}{Wonder Cure ‚Äì inflict status that once per battle revive to full from KO}{None}

\kskill{WEAKNESS}{Pick Locks}{Steal equipped items}{create decoy [follow pacifist AI]}{+5 to all flanking bonuses}{Create Shadow Clone [duplicates actions of main]}{create 2 decoys}{create 2 shadow clone}{None}

\kskill{CHARISMA}{Call Ally lv 1(quicken an ally to move next); Discount Lv1}{Convert Neutral Character (Requires 3 successful attempts w/o interference)}{Tag Ally (Switch places with out of battle ally for 3 turns,All effects and damage done to this ally transfer to Hero after 3 turns); Discount Lv2}{Call Ally lv2 (Preform a single action of an out of battle character)}{Convert Foe (Requires 3 successful attempts w/o interference); Discount Lv3}{Reinforce Ally (All allies get +2 modifier); Order Ally (Creates an ally that acts under AI for 3 turns)}{Double Soul (Combine with an adjacent ally into a single unit with total skill 
+1; if skill lv>5 then grant $\Omega$ skill)}{None}

\section{MAGIC}
Magic works using the difficulty system.  When a character uses a magic ability, they draw 2 cards.  The first card is the card bonus for the action.  The second card determines whether or not the caster will suffer manna burn.  This is determined by using the difficulty of the action.  If the rank of the second card is greater than or equal to the difficulty of the action, then the user suffers no manna burn; else, the user will suffer 1 damage as manna burn.  Each level that a character has in a given skill reduces the difficulty of using abilities in that skill by their skill level. For example, a character with Cast 4 who is using an ability with a difficulty of 12 from the Cast skill would need a 8 or better to succeed. However if the same character attempted to use a Heal ability, He would have to get a Queen or better to succeed.  Abilities that have enhanced manna burn will suffer the ceiling of ceiling (cost/5) damage.  For example the same mage casting the 12-difficulty spell except it dealt enhanced manna damage,the manna burn would be 3 damage.

\skill{CAST}{Bolt (9 difficulty),Block (9 difficulty),Level 1 Elements (+1 difficulty)}{ Sky Bolts (10 difficulty),Level 2 Elements (+2 difficulty),Elemental Specialty [grants special cast and -1 difficulty for the element; only one element may be specialized at a time]}{Blast (11 difficulty),Level 3 Elements (+3 difficulty),Empower magic [-1 difficulty for next cast; deductions stack i.e.3 uses yields a -3 difficulty for next cast]}{Wave (12 difficulty),Storm (12 difficulty),Level 4 Elements (+4 difficulty)]}{All Special Casts (difficulties vary)}{Difficulty -2 for Cast abilities}

\skill{HEAL}{Heal 1 (difficulty 8)}{Take Energy from magic from environment,Status heal (difficulty 9)}{Take Energy from ally or neutral unit}{Take Energy from foe,Cast 2 heal actions in one turn (+2 difficulty)}{ Revive from KO (difficulty 14),Cast 3 heal actions in one turn (+3 difficulty)}{Difficulty -2 for Heal}

\skill{ALCHEMY}{Enchant Element (9 Difficulty)}{Transmute item at 3:1 cost (10 difficulty)}{Transmute item at 2:1 cost (11 difficulty),Enchant Ability from Skill lv1 (10 Difficulty),Increase Skill level of enchanted ability by 1 level (+1 difficulty each level)}{Transmute item at 1:1 cost (12 difficulty),Enchant Ability Skill lv 1 (15 difficulty)}{Create Great Alchemy (Difficulty 19)}{Difficulty -2 for Alchemy}

\skill{SUMMON}{summon creature worth 3 points (10 difficulty),order creature}{Summon creature worth 5 points (11 difficulty)}{Summon creature worth 10 points (12 difficulty),sustain creature (+1 each turn sustained past 2)}{Summon creature worth 15 points (13 difficulty)}{Summon creature worth 20 points (14 difficulty),move while summoning}{Difficulty -2 for Summon}

\skill{STATUS}{Buff/Debuff 1 point any stat except will duration 3 (Difficulty 10)}{Remove Status (11 Difficulty)}{Recurring Buff
/Debuff 1 point duration 3 (Difficulty 12)}{Increase Duration by 1 (+3 each)}{Increase Intensity by 1 (+4 each)}{Difficulty -2 for Status}

\skill{MIND}{Passive share fog of war sight,communicate w/o line of sight
}{Inflict Knock back (11 Difficulty each)}{Preflex (Difficulty 15)}{Mind Wipe (ban use of all abilities from a skill for 3 duration; difficulty 13)}{Mind Control (chose one of next 5 actions,difficulty 14)}{Difficulty -2 for Mind}

\skill{GEOMANCY}{Move Panel new location (10 difficulty)}{Change panel type (11 difficulty)}{Change 3x3 area to panel type (12 difficulty)}{Change Conditions (13 difficulty)}{Release Panel Effect (14 difficulty)}{Difficulty -2 for Geomancy]}

\skill{SHAPE-SHIFTING}{Change elemental affiliation (difficulty 10)}{Change race (11 difficulty)}{Acquire additional racial area (Difficulty 12)}{Acquire additional Racial Skill (Difficulty 13)}{Acquire 3rd Racial Skill (Difficulty 14)}{Difficulty -2 for Shape-Shifting}

\section{MECHANICS}
\textit{Abilities in this tree may not be used if the user is below 1/3 full will.}

\skill{AI}{Memory 2; Learn Ability (2 Memory)}{Memory 4; Learn Skill (4 Memory)}{Memory 6; Learn Weapon (6 Memory)}{Memory 8; Improve Skill 1 level (3 Memory each)}{Memory 10}{Memory 16}

\skill{ENGINE}{Shift 1(move one attribute point from attack,defense,or speed to attack,defense,or speed);}{Shift 2}{Shift 3; shift movement type}{Shift 4}{Shift 5}{Teleport (uses 3 shifts to move in all remaining actions to a specific part of a round)}

\skill{INFECTION}{Deal 1 damage and heal 1 hp;}{Deal 1 damage and inflict recurring debuff (3,1,HP)}{Deal 1 damage and control foe‚Äôs next action}{Deal 1 damage and control foe until he or she is attacked}{Deal 1 damage and exchange a skill with foe.}{KO target after next round if user and target are adjacent}

\skill{EXTENSION}{+1 extensions; use one extension to increase Attack,Defense,or Speed; buff removed when user cannont use Extension}
{+1 extensions}{+1 extensions; +1 hand for 3 extensions}{+1 extensions}{
+1 extensions; +1 durability for all extensions for 2 parts}{for 2 extensions,+1 attack,defense,and speed}

\skill{DRONES}{Create Attack Drone (create 1 unit that ‚Äúattacks at will‚Äù with a short range weapon); Create Defense Drone (create one unit that ‚Äúdefends me‚Äù); the drone units are destroyed if the drone‚Äôs controller unit is hit.}{Create Heal Drone (create 1 unit that ‚ÄúDefends Team‚Äù that can heal other units); Create Long Range Drone (Create 1 unit that ‚Äúattacks at will‚Äù with a long range weapon)}{Create Movement Support Drone (create a unit that modifies another drone to have "flight"Äù movement instead of ‚Äúland‚Äù movement)}{Create Terraform Drone (Creates a unit that follows controller and changes tiles to a specific preset type)}{Create Command Drone (Creates a unit that allows the control of another drone as if it is an additional player character)}{Advanced Drone (Creates a unit that allows a drone take an additional action each turn)}

\skill{TRANSFORM}{Change element (takes 1 turn)}{Change Weapon (takes 2 turns)}{Change Armor/Foot/Helm (takes 2 turns)}{Speed up changes (-1 turns)}{Change skills (takes 4 turns; cannot be used to replace Transform)}{Speed up changes (-1 turns)}

\skill{FIELDS}{field radius 1; buff 1 attack,defense,or speed.}
{debuff 1 foe's attack,defense,or speed}{recurring buff (3,1,HP); negate conditions}{debuffs recurring foe'ôs HP}{field radius 2}{increase magnitude of effect by 1 unit}

\section{ANCIENTS}
Cool: a status that lasts a given duration that during which no Ancients skills may be used
Status: Ancient statuses for each skill are required to use all abilities in a skill 
\skill{DRACONIS}{Enable DragonRage (Duration lv
+2/ Cool 5) Attack (+lv)}{Claws (Wide cut + bleeding; +lv as bonus; -1 duration)}{Flight (status; cannot be targeted by short range weapons; duration -1)}{Dive ([lv-2] x short range attacks; duration -1; must be in flight)}{Breath (hits a triangle 3 deep; drains duration to 0; cool is +5 duration for next cool)}{Mega Breath (hits a triangle 5 deep with two Special Attacks; drains duration to 0; cool is +10 duration for next cool)}

\skill{HYDRONIS}{Enable SeaStorm (Duration lv+2/ Cool 5) Will cap (+lv)}{Venom (Long Range; inflict recurring debuff (-1,3,HP); +lv as bonus to hit; -1 duration)}{Regent (status; Heal 1 HP; duration -1)}{Frenzy (On hit,counter with [lv-1] x short range attacks; duration -1)}{Muramasa (Deals [Will cap-will] short range attacks; drains duration to 0; cool is 
+5 duration for next cool)}{Dark Counter (On hit,counters with Muramassa twice; drains duration to 0; cool is +10 duration for next cool)}

\skill{HUMONIS}{Enable LastStand (Duration lv+2/ Cool 5) Wield (Unlocks legendary powers on Ancient Weapons)}{Route (prevents targets next turn; +lv as bonus to hit; -1 duration)}{Level 3: Rally (Status; all allies with 1 hp move again; duration -1)}{Charge (Exchange actions with a teammate; -1 duration)}{Muster (Interrupt initiative and take ¬Ω moves rounded down before all others; drains duration to 0; cool is +5 duration for next cool)}{Artillery (take 1 long range attack on all foes; drains duration to 0; cool is +10 duration for next cool)}

\skill{DIMENTIA}{Enable VoidCast (Duration lv+2/ Cool 5) Negate Conditions}{Change all adjacent tiles to a specific tile set (-1 duration)}{Spawn Object (duration -1)}{Spawn Creature (Exchange actions with a teammate; -1 duration)}{Force of Will (Effects made during ancients mode become permanent; drains duration to 0; cool is +5 duration for next cool)}{Black hole (do 3 hits to adjacent enemies; do 2 hits to enemies 1 panel away; do 1 hit to enemies 2 panels away; pulls targeted units towards user; drains duration to 0; cool is +10 duration for next cool)}

\skill{CONTROLIA}{Enable LuckyStreak (Duration lv+2/ Cool 5) +lv to all actions}{+3 luck (duration -1)}{Even Luck (status; redraw lv or less; duration -1)}{Good Luck (Draw two and take average; -1 duration)}{Strong Luck (Draw 3 cards and take highest for card bonus; drains duration to 0; cool is +5 duration for next cool)}{Miracle (Automatic Joker for next action; drains duration to 0; cool is +10 duration for next cool)}

\section{Drifting}
Drifting abilities may only be used on portals.
\skill{Space}{portal allows transport between 2 portals}{User may exit anywhere on the map (1 mp)}{Open Portal at distance (1mp)}{Force enemy to enter portal(1mp)}{Transport all allied units adjacent to portal(2mp)}{Force all enemy units to enter adjacent to portal(2mp)}

\skill{Time }{Portal (+1 initiative)}{move target character up or down one position in initiative.}{Enlarge Portal}{Stop (Caster and target cannot act next round)}{Quicken -Target gains an additional action at the end of the turn order.}{Quicken Party - allies gain an additional action}

\skill{Ancient}{Portal (+1 power level but user can only use default abilities)}{Player may use skills instead of default abilities}{+2 Power Level}{Expand Portal}{Follow Portal}{+3 Power Level}

\skill{Dream}{Portal (Prevent 1 debuff from having affect)}{Target gains debuff on card bonus}{Prevent critical hits on target}{Expand Portal}{For target, treat 3's as a -2}{Target suffers 2 damage/hit}

\skill{Dark}{Portal takes will from adjacent allies for a buff}{Expand Portal}{Take will from allies to heal the enviroment}{Corrupt World - drifters with out dark drifting take 1 damage while drifting}{Hits do 2 damage but deal 1 damage recoil}{Player can continue to attack as long as they can target a new unit}

\skill{Arcane}{Portal heal environment or self at 3:1 environment:self ratio}{can now target allies}{Expand Portal}{can now target foes}{Gaia's link: target transfers will to environment each round or visa versa}{Abilites in this tree are now range 2}

\skill{Cyber}{create portal(user may place/dispel a block adjacent to portal) users with cyber drifting may attack through block}{user may knockback a block when on a portal}{user may create a line of blocks from the portal to a existing block}{user may move to any space adjacent to a set of adjacent blocks to which he is adjacent}{User transforms block to copy next attack}{User chain transforms blocks to copy next attack}
\skill{Kinetic}{Portal + lv to strength}{Disables (Force Repair;  Force Manaburn; -3 duration ancients)}{Beam (seeks to hit target) }{Follow Portal}{"jump" over foes from portals}{Spirit Blast ‚Äì Wait n turns; deals n damage to n radius panels from user; if attacked during wait reset n to 0}


\section{RACIAL}
\textbf{STRENGTH}
The Strength level is multiplied by 2 and added to all attacks\\
\textbf{DEFENSE}
The Defense level is multiplied by 2 and added to all defenses\\
\textbf{SPEED}
Speed has 2 functions.  First when players draw for initiative,add the speed multiplied by 2 to the card bonus.  Second,if the initiative value for any hero is 15 or greater; then the Hero takes 2 actions per round.\\
\textbf{WILL} Will level is added to 6 for a characters Will Cap.
%\end{multicols}

\chapter{THE STAR JOURNAL}
\section{WHISPS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Life
Class: Light Race
Racial Area: Magic
Racial Specialty: can use all magic at -2 difficulty
\subsection{PHYSIOLOGY}
\subsubsection{GENDER}
The Whisps are androgynous.  They reproduce by budding.  Whisps bud every 10 a years on the summer solstice.
\subsubsection{LIFE CYCLE}
The average Whisps live for about 30 years with a standard deviation of 5 years.  As the Whisps age,their body temperature grows.  Whisps are considered to be young until their first budding.  Growth-wise,the Whisps are fully developed after the first year of life.  Development-wise,the Whisps are not fully matured until their first budding.  The gap between physical and mental development causes conflict because the youth are eager to act,but often do not have the sense of mind in order to act properly.  During the middle phase (from the 1st budding to the 2nd budding),the Whisps are at their physical prime.  During the last stage of life,the Whisps temperature slowly levels off.  When the Whisps die,their flame slowly fades until they die.
\subsubsection{HEIGHT AND WEIGHT}
The core of the Whisps body is a sphere that is 40cm in diameter.  As the Whisps age their trail ranges from 20cm to a meter in length.  The Whisps weigh about 20kg.
\subsubsection{ANATOMY}
The Whisps are constructed of plasma-like substance that is constructed in two main components.  The core is a sphere about 40cm in diameter.  The core is where most core functions of the Whisps take place.  The nervous, vascular, and digestive systems are located in the core.  The nervous system of the Whisps is remarkably developed to allow seamlessly interface with the Destiny system.  The Whisps use this system to as their primary means of locomotion as well as interacting with their physical environment.  This highly developed nervous system is also how the Whisps sense their environment.  Because the sensory system is not dependent on light, sound, or contact, the Whisps have extraordinary senses.  Their vascular system is an open vascular system with convection within the core being the primary means of circulation.  The digestive system produces energy by engulfing foreign objects and using chemical combustion reactions to extract the energy from the objects.  The other body structure is the trail.  It contains the reproductive organ where budding Whisps are developed.  The trail also contains a crystal encased nerve.  This nerve acts as an antenna for the central nervous system allowing the Whisps to extend their sphere of influence.  Other than the nerve in the trail, the Whisps do not have any internal structure.  The dermis of the Whisps is constructed of the same crystalline substance that coats the spine and is hot to the touch.  However, the dermis does not provide much protection from physical damage as the in depth integration with the destiny system is the primary method of defense.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Whisps tend to be peaceful towards other races.  This is mostly because while they can defend themselves,they can become easily overwhelmed due to their lack of physical defense inhibit and their 
\subsubsection{ECONOMY}
The Whisps use a market economy.  They specialize in enchanting materials produced by other groups.  The Whisps also use their superior intelligence to perform design and engineering work.  However,the high levels of intelligence and relatively fast reproductive cycle leads to an enormous highly qualified labor force that is competing for a comparatively small number of jobs.
\subsubsection{OCCUPATION}
The Whisps fulfill mostly tertiary sector jobs.  They specialize in engineering,energy,and product refinement.  Their engineers are some of the best of all of the races.  They focus on elegance in design.  Their work is considered to be exceptionally reliable and functional but not without cost.  The Whisps have a large energy sector.  They work to produce energy through Magic fueled energy systems.  The Whisps also work in product refinement.  Whips alchemists are considered to be highly skilled in their field.  
\subsubsection{LEISURE}
The Whisps have a large variety of leisure activities.  Many activities involve modifying games played by other races to require the use of magic.  For example,the Whisps play a ball game where the ball may only be struck with bolts of magic above a field where the players are flying around.  The Whisps also enjoy crafts and art.  One especially popular technique is to embed moving images into gems using magic.
\subsubsection{EDUCATION}
The Whisps educate their young by transmitting knowledge using magic through the antenna in the trail.  This allows huge and effective data throughput, but is exhausting for both the teacher and pupils.  Primary and Secondary education takes place in the first 3 years of life.  The Whisps School is often scheduled only once a month.  After the first 3 years the Whisps then are apprenticed for the next 5 years in a variety of different areas.  During this time, the Whisps will explore a variety of different career paths until they find one that they have great skill.  After a career path is chosen, the Whisps begin a two year long application process as they compete for positions in the best companies.  Then only the most talented are given jobs, the rest often emigrate to find work.
\subsubsection{GOVERNANCE}
The Whisps are governed by a Republic.  The laws ensure equality of opportunity for its citizens and provide a frame work to resolve disputes.  The laws are enforced by old magic powered by the life force of all Whisps.  The fact that the laws are enforced consistently across all Whisps and mediated by an exterior force prevents tampering and allows for an efficient and minimalist government.
\subsubsection{FAMILY}
The Whisps place moderate importance on the Family unit,but greater importance on the community.  This means while the Whisps respect and appreciate their parents from which they bud,The Whips place greater importance on the overall wellbeing of the society in which they live.
\subsubsection{HISTORY}
No one knows when or why the Whisps were created.  The oldest records that exist do not even include the formation of the Republic which happened in the early days of their race.  The Republic has ruled for many generations and likely will continue to rule.  Occasionally there are young Whisps who wish to dismantle the Republic by unraveling the wards that hold it in place; however, these efforts have been unsuccessful due to the fact the wards are tied to the lives the Whisps.  The Republic has successfully defended itself against invasions of opposing races including the Zar?ock and Navicos.  The Navicos invasion was short lived.  Some historians have argued that the invasion was actually aggressed by the Whisps and the Navicos were simply exploring.  Whisps would argue extensively that this is simply not true.  The Zar?ock continued their efforts for several generations before being successfully driven away.  These invasions left the Whisps strongly cautious of any actions by these two races.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Whisps generally follow a lawful alignment
\subsubsection{GOALS}
The goals of the Whisps are:
\begin{enumerate}
\item To continue their own existence
\item To enjoy life through self-perfection
\end{enumerate}
\subsubsection{FOES}
The Whips do not actively seek out foes; however,they have and do fight to defend themselves.  Their primary enemies include races that have the physical prowess to overtake them such as the Navicos and Zar‚Äôock.
\subsubsection{TEMPERAMENT}
The Whisps tend to have a short temper.
\subsubsection{ATTITUDE ON LIFE}
Whisps view life as a time to explore.  There is nothing before or after.
\section{NAVICOS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Sea
Class: Light Race
Racial Area: Magic
Racial Specialty: Strength +2
\subsection{PHYSIOLOGY}
\subsubsection{GENDER}
The Navicos are Male and Female.  The Males are slightly larger than the females.
\subsubsection{LIFE CYCLE}
The Navicos live on average 80 years with a standard deviation of 10 years.  The Navicos are raised by their family until age 10.  The Navicos are completely physically and mentally mature around age 20.
\subsubsection{HEIGHT AND WEIGHT}
The Navicos are on average 1.75 meters tall.  They weigh approximately 90 kg.
\subsubsection{ANATOMY}
The Navicos have two arms and two legs.  They walk primarily upon their two legs, but they can sprint using all four limbs. The Navicos are completely covered in blue fur with darker stripes.  This fur aids them in camouflaging themselves in the water.  Under the fur is a thick rubber-like skin that helps to seal in water.  The Navicos have superior vision and hearing facilitated by their larger eyes and ears.  The Navicos have claws that grow above their hands and feet.  They use these claws for a variety of purposes.  The toes of the Navicos are webbed to facilitate faster swimming. Compared to other races, the Navicos have considerable muscle mass. Internally, the Navicos are mostly unremarkable.  Their features are similar to humans with the exception of the respiratory system.  The Navicos have an additional pair of diaphragm muscles that can be used to quickly clear water from the lungs.  The respiratory system is also capable of processing larger amounts of oxygen and of filtering out carbon dioxide more efficiently.  This allows the Navicos to survive for extended periods of time under water.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
The Navicos are geological explorers by nature and natural drifters.  This has both helped and hindered their relations with other races.  One notable example occurred when a Navicos ship landed in Whips territory.  Seeing the action as an act of War,the Whisps attacked.  The willingness to not occupy territory has allowed the Navicos to form workable relationships with the Zar‚Äôock and Tessaran.
\subsubsection{ECONOMY}
The Navicos economy is primarily funded by trading with other races.  The Navicos are premiere navigators and ship builders.  They use these skills for a price for any race seeking transport.
\subsubsection{OCCUPATION}
Navicos earn their income by serving on ships.  Hence,they spend most if not all their life onboard ships.  These ships have a variety of roles ranging from cook,quartermaster,and captain.  The exact number and variety of roles depends on the ship.  However,one role is always filled: the Navigator.  The Navigator serves as an advisor to the captain.  It is the most respected role on a ship even more so than the captain.  The Navigator reminds the crew of their duties to the world around them and to their souls.  The Navigator encourages the crew to seek the Creator in all they do.
\subsubsection{LEISURE}
There is extensive time available on a ship on a long voyage.  As such the Navicos are constantly searching for ways to entertain themselves.  They enjoy mostly sports and shun the academic.  Young Navicos will compete in tests of strength.  
\subsubsection{EDUCATION}
The Navicos are educated in a teacher-apprentice manner.  This process is quite lengthy.  They learn what ever skills they need to complete their current role and little more.  However,they are typically adept at whatever they put their effort towards.  Over their lifetime a Navicos may have 3 teachers.
\subsubsection{GOVERNANCE}
The Navicos do not have a centralized governmental structure.  Instead each ship operates as an independent body.  There are 4 authority figures on every ship: the Captain, the Purser, the Quartermaster, and the Navigator.  The Captain has sole executive authority.  He decides what tasks the ship will pursue and how they will be pursued.  The Purser is the keeper of all funds.  He is responsible for paying all hands aboard ship and has the sole authority to remove the Captain from his post.  The Quartermaster Is the second in command of the ship and responsible for all cargo aboard ship.  The Navigator serves as an advisor.  The Navigators travel from ship to ship leading their ship.  They are exempt from the Captain?s authority but rely on the crew for their wellbeing.  The crew decides the pay of the Navigator at the end of the Voyage.
\subsubsection{FAMILY}
The family structure is important for the first 20 years of a Navicos‚Äôs life.  After this time period,the Navicos leaves his family and he or she serves his or her Captain solely.
\subsubsection{HISTORY}
The Navicos are another very old race.  The most important element to the Navicos history is the history of the Navigators.  According to records,the ships of the Navicos once traveled without Navigators.  These early ships would often fight and dispute causing severe damage to all involved.  Eventually a group of young Navicos sought to end the violence.  They found an old book with faded gold lettering on the cover floating in the sea.  The Navigators were fascinated by its message and spread it to the crews.  The crews of these ships mutinied against their wicked captains,and the captains were relieved by the pursers.Since then the ships have been peaceful and a Navigator is always on board.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
The Navicos are Lawful and Good.
GOALS

\begin{enumerate}
\item Keep the commandments of the book of the Navigator
\item Obey the Captain
\item Fulfill the Charter
\end{enumerate}

\subsubsection{FOES}
The Navicos tend to be happy go lucky and do not have major enemies
\subsubsection{TEMPERAMENT}
The Navicos are easy going
\subsubsection{ATTITUDE ON LIFE}
Life is a sacred gift of the Creator


\section{TESSARN}
\subsection{BASIC INFORMATION}
Elemental Alignment: Electric
Class: Light Race
Racial Area: Mechanics
Racial Specialty: Can have up to 6 skills.  The 6th skill is stored and can be switched as an action.
\subsection{PHYSIOLOGY}
\subsubsection{GENDER}
Tessarn are hermaphroditic.  There must be at least two Tessarn for procreation to occur.  
\subsubsection{LIFE CYCLE}
The Tessarn have two life cycles that occur concurrently.  First the physical life cycle occurs over a period of 5 years.  Second the psychological life span takes place over a period of on average 100 years with a standard deviation of 10 years.  While the physical body will die, the psychological conscious will be transferred to the next body at the time of physical death.  The twin nature of their life cycle is important for several reasons.  Firstly, the Tessarn can change their physical appearance to adapt to the environment around them.  For example, if the Tessarn enter an environment with large quantities of water it can adapt its form to include flippers and other adaptations that allow it to thrive in its new environment.  Secondly, because the psychological conscious does not change with the physical body, it allows the Tessarn to learn from the past experiences from each iteration of its physical form and not has to relearn information between after iteration.    
\subsubsection{HEIGHT AND WEIGHT}
Tessarn dimensions vary greatly.  They typically range from .5 meters tall to as tall as 2.5 meters tall.  Their weights range from 5kg to 200kg.
\subsubsection{ANATOMY}
The Tessarns have an extremely veritable anatomy.  There are some common components.  First there is a core.  The core is cylindrical in appearance and houses the psychological conscious of the Tessarn, its memory, and the genetic information of the physical form of the Tessarn.  The memory and genetic information are stored as digital information within the Tessarn.  Ports on the base of the cylinder are the means of data transfer between two Tessarn that allow for data transfer and reproduction.  The physical body changes every 5 years and rarely stays constant.  It is typically constructed from organic materials using advanced chemical processes; however, in extreme climate situations, the Tessarn can produce a non-organic physical form.  The changes are often drastic and allow the Tessarn to quickly adapt to the environment around them.   Even the digestive and respiratory systems can completely change.  A Tessarn can be a Carnivore before iteration and an Herbivore after the iteration.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
As a whole,the Tessarans will quickly change their relationships in order to maximize their current situation.  For example if an associate suddenly becomes unpopular,it is not uncommon for it to be abandoned.  If someone becomes popular the Tessarn will quickly begin to wheel and deal to become in that individual‚Äôs good graces.  This has earned the Tessarn a reputation as untrustworthy amongst most races.
\subsubsection{ECONOMY}
The Tessarns will quickly change their economy and mode of economy to adjust to their current environment to maximize their profits.  In situations where a socialist economy is most effective for the whole it will be employed.  In situations where a market economy is most effective it will be used.  Tessarns tend to be short sighted in their planning making the best use of what works now in order to be successful.  The changes in their economy tend to line up with their 5 year iteration cycle.
\subsubsection{OCCUPATION}
Tessarn are extremely well adaptable to any job they are put to.  The Tessarn will optimize themselves to complete the tasks they need to complete when they physically iterate every 5 years.  Outside of their specialty,the Tessarn tend to be mostly useless.  They are generally gifted with the area of technology but even this can be rotated out of their abilities to make room for other abilities as the need arises.
\subsubsection{LEISURE}
Leisure is seen as a waste of time and resources.  The Tessarn are strictly functionalist.
\subsubsection{EDUCATION}
Tessarn use the same data transfer protocols used to transfer their genetic information to transfer to other Tessarn.  Any further education is seen as a waste of time and energy.
\subsubsection{GOVERNANCE}
The Tessarn view governance as a waste of time and energy.  The only law that governs them is the survival of the fittest.
\subsubsection{FAMILY}
Time spent raising offspring is seen as a waste of time and energy.   There is not a family structure.  
\subsubsection{HISTORY}
The Tessarn arose from an artificially intelligent robotics experiment.  As the time passed the Tessarn began to be completely autonomous.  Eventually the Tessarn developed organic computing and their modern form developed.  There are some Tessarn that object the short-termism of the Tessarn as a whole.  These Tessarn tend to be more successful in the long run however are often criticized for not be as adaptable as the other members of their race.  These individuals are highly respected by other races for their actions but tend to not receive the same respect at home.  Over time the majority of Tessarn have attempted to phase out the more long-term orientated Tessarn but have been unsuccessful not seeing an incentive for anything more than a passive effort to eliminate them.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Lawful
\subsubsection{GOALS}
To achieve optimal performance.
\subsubsection{FOES}
The Tessaran have no distinct foes but they also do not have any distinct allies either.
\subsubsection{TEMPERAMENT}
Tessarn have whatever temperament best suits the situation they are in.  Logic is valued and Emotional action as a whole is seen as inefficacy.
\subsubsection{ATTITUDE ON LIFE}
Life exists to produce a better next generation.
\section{ZAR'ÄôOCK}
\subsection{BASIC INFORMATION}
Elemental Alignment: Earth
Class: Light Race
Racial Area: Magic
Racial Specialty:  Can use long range attacks without a long range weapon
\subsection{PHYSIOLOGY}
\subsubsection{GENDER} 
Zar‚Äôock are male and female.  They reproduce by the female laying eggs that develop in the nest.
\subsubsection{LIFE CYCLE}
The Zar?ock life cycle begins at the egg.  The eggs grow in nests of hundreds of eggs.  After about 6 months in the eggs, the larval form will emerge.  The newly hatched larvae are extremely hungry.  They will eat the first thing they see; even if the first thing they see is one of their fellow hatchlings.  After a few hours around a hundred larvae remain.  These Larvae quickly learn to survive.  They are born with an innate battle instinct.  After assuring a source of food, the Zar?ock will begin to form a web and fashion tools.  This stage will continue for several years.  After about 30 years the Zar?ock will mature.  At this time, they will have developed a large web and sizable arsenal of weapons.  Some Larvae will go through a metamorphosis.  The metamorphosis process takes only a few hours.  After metamorphosing, the Zar?ock emerges fully developed and matured with large wings and are overall far more dangerous.  Only Zar?ock that metamorphose are capable of reproducing.  At about 50 years of age the Zar?ock dies.  When they die they are often used to feed the next generation.
\subsubsection{HEIGHT AND WEIGHT}
Zar‚Äôock are 3 meters tall in the larval stage and 5 meters tall in their metamorphosed state.  They weigh 1800 kg and 3600 kg respectively.
\subsubsection{ANATOMY}
The anatomy of the Zar?ock differs on two factors: state of life, and sub species.  Within each state of life there are only slight differences between subspecies.  The larval stage has 10 limbs: 8 legs and 2 arms.  The body stands erect on all eight legs and uses the arms to perform a variety of tasks ranging from devouring foes to wielding weapons.  The adult stage has 16 limbs 8 legs, 4 arms, and 4 wings.  Both types have the same type exoskeleton.  The exoskeleton makes them incredibly strong.  They have 8 eyes arranged on the head portion of the exoskeleton.  These eyes allow the Zar?ock to see almost all the way around themselves without turning their head.  Only 30 degrees directly behind the head is not visible.  Internally, the Zar?ock have an unremarkable digestive, open circulatory system, and respiratory system.  The digestive system has a distinct feature.  In addition to its normal function, the digestive system will allow the Zar?ock to process their food into web.  The web is remarkably strong.  The Zar?ock use this web both to secure pray but also as their primary building material.  The Zar?ock are mildly intelligent and are capable of communication and problem solving. The Adult form has the same features except it grows an additional pair of arms and 2 sets of wings.  These wings are used to transport the Zar?ock short to medium distances in pursuit of their prey.  There are 6 distinct subspecies.  Each subspecies can be identified by the unique coloring of their exoskeleton.  Reds have slightly stronger arms and thicker exoskeletons.  They primarily serve as guards for the web.  Blues have superior eyesight and fine motor skills.  They are capable of wielding bows with ease.  They serve as snipers taking out foes with the bows and web.  Yellows are the fastest.  They have the ability to paralyze their foe with a venomous bite.  Greens have the thickest exoskeleton and are the most intelligent.  Their increased intelligence gives them an aptitude for magic.  Whites are rarer and are the queens of the web.  They have the strongest web.  They have additional glands that secrete powerful hormones that can both seduce prey and call hordes of Zar?ock to their aid.  Blacks are the Kings by far the rarest.  They have the all of the preceding characteristics plus an unquenchable blood thirst.  Even other Zar?ock tends not to like King Zar?ock.
	One would be remiss to avoid taking about the importance of the web to the anatomy of and function of the Zar‚Äôock.  It functions almost as an extension to the Zar‚Äôock that it houses.  The Webs are enormous cavernous structures.  Zar‚Äôock store food,lay eggs and preform most of their lives within the walls of the web.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Zar‚Äôock have poor relations with other races.  Only Greens even consider the regularly consider the possibility of working with other races.  These relations are often tempered with the knowledge that the Zar‚Äôock are known to eat those they don‚Äôt like.
\subsubsection{ECONOMY}
All actions with in a web are centered on the Queen and possibly King of the Web.  They will likely request items be built to suit their needs or to fulfill needs within their webs.  For example tools could be build that are then rationed out to the others in order to defend the web or build a large object.
\subsubsection{OCCUPATION}
The Zar‚Äôock often work in serve of their king or queen.  Whatever he or she asks them to do they often will do it.  Outside of the webs of kings and queens,the Zar‚Äôock are skilled mercenaries and smiths.  The Greens are even moderately skilled mages.
\subsubsection{LEISURE}
The Kings and Queens will often laze about doing whatever pleases them.  They enjoy mostly carnal pleasures such as gorging themselves on food or torturing their underlings in a variety of ways.  Occasionally a King will lead its forces into battle; however,this is uncommon albeit terrifying experience.  In free webs,the Zar‚Äôock will mostly play sports and occasionally study culture and history.
\subsubsection{EDUCATION}
Zar‚Äôock are not educated.  If they die as a result they are viewed as not worth the effort anyway.  Very seldom,a queen or a green will learn to read and study cultures of other races but this is uncommon even in the free webs.
\subsubsection{GOVERNANCE}
The queen strongly influences the actions of the other Zar‚Äôock through her hormones.  To them,her secretions are a highly addictive drug.  Zar‚Äôock that are exposed will experience an unimaginable high but will also go through severe withdrawal just hours later even after one exposure.  To this end the queens will withhold this addicting serum in order to get what they want.  Often Queens will never work and will have their slaves construct huge webs for them.  Kings behave in much the same way except they often work to steal and kill for their spoils.  In free webs,the Zar‚Äôock are ruled by a total democracy.  As there are relatively few of them,this works well.
\subsubsection{FAMILY}
Zar‚Äôock have no family aside from the unshakable loyalty to their King or Queen.  In the free webs,Zar‚Äôock treat the entire community as extended family with their specific subspecies as family.  The oldest female is considered the leader of this family.
\subsubsection{HISTORY}
The Zar?ock are a very old race.  They have existed since the beginning of creation much to the detriment of other societies.  After several generations, the first queens were born.  They used their chemical charm to build large webs.  Despite the oppression their underlings endured, The Zar?ock flourished during this time and many of their now greatest skills were developed.  After several millennia, a King was born.  The king started a great war against the other races.  This war led to the Zar?ock taking over large territories.  After the king passed, the other races reclaimed much of their lost lands.  In the few Kings who have lived since, each has attempted to reclaim the glory of the first King.  This also led to the creation of several distinct hordes of Zar?ock as the races were often unable to completely remove the Zar?ock from their previous territory.  Eventually a small group of Greens and other Zar?ock were able to escape addiction.  They formed their own democratic web.  Without the addictive hormones to ensure cooperation, their web has faced many problems, but their civilization is the most developed of any Zar?ock horde.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Kings,Queens,and Others: Evil
Free Webs: Neutral
\subsubsection{GOALS}
Queens and Kings: To have the most property than any Zar‚Äôock ever
Others: To serve the King or Queen.
Free Webs: to live life to the fullest
\subsubsection{FOES}
Almost all races hate the Zar‚Äôock.  Few races will even agree to live near free web Zar‚Äôock for fear of attack.
\subsubsection{TEMPERAMENT}
Zar‚Äôock have horrible tempers.
\subsubsection{ATTITUDE ON LIFE}
Life here and now is all there is.
\section{DRAS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Earth
Class: Light Race
Racial Area: Ancients
Racial Specialty: Can access Mechanics Abilities
\subsection{PHYSIOLOGY}
\subsubsection{GENDER }
The Dras are androgynous.They reproduce by budding from the body of a dying Dras.  Dras usually only produce one offspring; however,the older the Dras the more offspring it will produce upon its death.
\subsubsection{LIFE CYCLE}
The average Dras lives for about 10,000 years with a standard deviation of 1000 years.  Because of their long lifespan they measure their age in centuries.  They refer to centuries as cycles.  Each cycle is divided into 100 clicks.  Dras are considered to be young from birth to about 20 cycles.  During this time, Dras are relatively weak and if killed during this time period, are unable to reproduce.  As a Dras approaches its 20th cycle, it will go through a stage where it becomes able to bud offspring.  This process is very painful for the Dras.  It will experience great growth.  The growth of a Dras consists of the development of its muscles and its mind to its adult stage.  Until a Dras reaches this point in its development, it is only capable of feeding and listening.  It is otherwise unable to act.  However after its metamorphosis, it gains great strength, stamina, and ability.  A Dras will continue to experience minor growth and development until its 80th cycle.  At that point in its life cycle, it will halt development.  Dras that live to beyond their 100th cycle begin a second metamorphosis.  Unfortunately, many Dras die during this process; hence, the average life span of 10,000 years.  After the second metamorphosis, the upper limits on a Dras's power disappear.
\subsection{HEIGHT AND WEIGHT}
Dras are on average 1.5 meters tall and weigh about 150 kg.
\subsubsection{ANATOMY}
Their anatomy is humanoid except they have 4 arms and 2 legs.  Their skin is a hard exoskeleton that serves as a heat-sync, photo voltaic cell, and an oxygen scrubber.  The exoskeleton is very dense but has blood vessels in complicated networks just below the surface to cool blood and assist with the energy production process. Under the exoskeleton, Dras has several body systems. They have a vascular circulatory system except it contains several smaller ?hearts? located at the periphery of the chest cavity that assist the primary heart located in the abdomen at pumping blood around their bodies.  Their respiratory system is located in their exoskeleton tiny pores located allow over the Dras allow gas to enter and then be processed by powerful cleaning cells.  The Dras do not have a digestive system; instead, their exoskeleton contains photo voltaic and photo chemical cells that produce chemical and electrical energy directly for use by the body.  The Nervous system of the Dras is distributed across the entire organism; however a core located in the midsection of the organism processes sensory information and processes goal oriented behavior.  The Dras use the differing light quantities coming into their bodies to determine visual surroundings, and a similar process is used to determine sound.  The Dras have a high powered energy core in their chest.  This is where unneeded energy is stored, and where after the 1st metamorphosis, atomic fusion is used to produce the chemicals needed to sustain the Dras's life.  Until the 1st metamorphosis, the Dras lives off a reserve from its predecessor.  The immune system of the Dras is also very potent.  All foreign particles are passed to the energy core and decomposed into new particles eliminating any threat of infection.  After the 1st metamorphosis, an organ develops that begins to create the Dras that will bud from the current Dras after its death.  After the second metamorphosis, the Dras lose their hard exoskeleton.  The Dras that survive use the fusion source in their chest to develop a new exoskeleton.  This process exposes the Dras to infection and other life-ending effects; hence, many do not survive.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Dras are fiercely independent.  They will not interfere with other races.
\subsubsection{ECONOMY}
The Dras have little need for economy because they can synthesize anything they need.  However,if it must it can make a bargain with another Dras or another creature; they will exchange pieces of their fusion sparks.
\subsubsection{OCCUPATION}
Dras do not have formal occupations because they do not have an economy.
\subsubsection{LEISURE}
Dras do whatever they determine is best for them.
\subsubsection{EDUCATION}
Dras are fiercely curious.  Dras observe the world around them to learn.  They have near perfect memory and have no need of a formal education system.
\subsubsection{FAMILY}
Dras have no family because unless its parent Dras survives its second metamorphosis,it will not have any living family.  Dras that are born as twins will never separate willingly.  They behave more as one organism with two bodies than two separate organisms.
\subsubsection{GOVERNANCE}
The Dras are governed by a council of 5 twice ascended Dras.  They are not governed in the general sense of the word.  The council is more of an advisory body.  The councils make decisions; however, each Dras is capable to disregard the decisions of the council at will.  This disregard is a rare occurrence but can happen.  Four of the members of the council represent the four cardinal elements.  The final member of the council name is Dracorum Chronos.  He acts as the leader of the council.  He is a powerful time mage and the only mage ever to master complete control of time travel. The Dras Council is notorious for its deliberate action.  No action is ever taken without extensive thought and discussion.  In order for a decision to be made all five must agree.  
\subsubsection{HISTORY}
Dras have existed since before the time before.  They are remains of an old prototype of the Destiny System that appeared to have failed.  They were discarded by the scientists as failed experiments.  However, during the process of disposal, they suddenly gained consciousness.  The Dras do not view the scientists who made them as their creators.  They believe that even though the scientists may have assisted in their awakening, it is far beyond their ability to create the marvels of the Universe.  They instead search all of time and space in order that they may find what they believe to the one true Creator.  Since their awakening, the Dras have lived alone in any part of the multi-verse they can find.  They observed the other races to learn their skills and abilities however never interfere with their subjects.  The Dras feel that naturalistic observation is the only method that produces reliable results.  After several generations of Dras, There were 5 Dras who had survived the second metamorphosis named: Chronos Dracorum, Prometheus, Gilgamesh, Thundolom, and Gaius.  Each specializes in their own elemental abilities: justice, life, sea, sky, and earth respectfully.  Each also focuses their studies on a specific area of the multi-verse.  Chronos Dracorum being the oldest, wisest, and most deliberate by far of his kind watches the development of civilizations throughout all of time.  Prometheus the youngest takes personal interest in the lives and interactions of different beings.  Gilgamesh the creative watches the majesty and beauty of the sea.  Thundolom the knowledgeable takes sentinel over the sky and space?s great mysteries.  Gaius the solemn often remains even more alone than his fellows as he watches over the vast expanses of land in the wilderness.  These Dras decided it was best for them to form a council to protect each other and their kind.  While each of these five Dras is rarely together, they will meet to defend their own and to prevent any catastrophe that could endanger Dras kind or life in general.  They have never worked with other races and many other races even deny the Dras exist.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Dras are Lawful Neutral and Non-Interventionist.
\subsubsection{GOALS}
Dras have three goals
\begin{enumerate}
\item To peruse knowledge of all forms through nonintervention to find and know the Creator
\item To prevent the destruction of the life of others to the extent that it does interfere with the first goal
\item To protect themselves only to the extent that it does not interfere with the first two goals
\end{enumerate}
\subsubsection{FOES}
The Dras Council is sworn enemies of the Sards who the Dras view as inferior copies.  They despise the constant intervention of the Sards into life that interrupts their naturalistic observation.
\subsubsection{TEMPERAMENT}
The Dras have an even temperament that comes from cycles of living
\subsubsection{ATTITUDE ON LIFE}
Life is the most valuable gift of the Creator
\section{EMITS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Sea
Class: Light Race
Racial Area: Ancients
Racial Specialty: Can copy another race‚Äôs specialty
\subsection{PHYSIOLOGY}
\subsubsection{GENDER }
Male and Female:  Those who drown while attempting to cross the waters of time are reborn as Emits.  They lose their own memory in the process.  Despite the existence of two genders they cannot reproduce.
\subsubsection{LIFE CYCLE}
Emits are immortal creatures,but they can be killed by sustaining fatal damage.  They only have an adult stage; however,their apparent age is directly tied to the time period they currently occupy.  In the time of before,they appear as infant child of the race they are currently imitating.  In the time of the past,they appear as young children of the race they are currently imitating.  In the middle ages,they appear as adolescents of the race they are currently imitating.  In the present,they appear as adults of the race they are currently imitating.  In the future they appear as elders of the race they are currently imitating.  
\subsubsection{HEIGHT AND WEIGHT}
Emits copy the height of the race they are currently imitating.  Emits weigh about 50 kg despite the form they currently hold
\subsubsection{ANATOMY}
Their anatomy changes to match the race they are currently intimating.  While alone or with only other Emits,they appear as white formless humanoids.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Because Emits copy the appearance of other races when they are around them,they have no specific racial agreements or disagreements.
\subsubsection{ECONOMY}
They copy the economy of the race they are living with.  When alone,they will barter if necessary.
\subsubsection{OCCUPATION}
They copy the occupation of the race they are living with.  When alone,they will specialize in a specific task they have done before.  Often,they fill government positions or serve in the tertiary job positions.  One group of Emits tasks themselves with the task of restoring time to its normal flow as well as preventing blockages of its flow.  Another group writes a text known as the Star Journal that is a record of all life in the multi-verse.  This group is very stoic in its efforts to ensure that nothing is missed.  It is considered an honor to be a member of this group.
\subsubsection{LEISURE}
They copy the leisure of the race they are living with.  When alone,they will spend time swimming and participating in other aquatic activities.  Emits will often spend extensive periods of time reflecting the events of the day and the actions of others.
\subsubsection{EDUCATION}
They have vast knowledge from the water of time and see no need for formal education.  However,they will participate in the educational systems of other races both as teachers and students in order to fit in as necessary.
\subsubsection{GOVERNANCE}
The Emits operate under a dictatorship.  The dictator is a very old creature known as the Chronos Dracorum.  It is a living embodiment of time.  Under the Chronos Dracorum, there are 3 lieutenants: Ergas, Luilas, and Argem.  Each supervises an aspect of emit life.  Ergas is the Great Historian.  He keeps is responsible for all of the records contained in the Star Journal.  He and his followers work to record detail accounts of history.  Luilas is the Great Guardian.  He is the enforcement arm of the Emits.  His followers work to protect as many beings as possible by actively interfering with time.  He and his followers were banished from the fountain of time for their actions by the Chronos Dracorum and Argem, but some Emits are sympathetic to his cause.  Argem is the Great Rememberancer.  He and his followers work to ensure that the Chronos Dracorum?s will is carried out in his absence.  He often opposes the actions Luilas and occasionally Ergas for their interference in time.
\subsubsection{FAMILY}
They copy the family life of the race they are living with.  Emits have no families on their own.  They live as a huge single-family units.
\subsubsection{HISTORY}
They exist from the flow of time.  The Emits follow a twice metamorphosed Dras known as Chronos Dracorum.  This Dras was a master of time magic and uses the form of a large dragon as its exoskeleton.  The Emits are the result of his fusion-spark interacting with the time stream.  Chronos Dracorum created the Emits to assistant him in his mission to observe the universe.  The Emits prospered under the rule of Chronos Dracorum benefitting from his vast knowledge and leadership.  Chronos Dracorum realized that the Emits were becoming more and more sentient.  He felt that he could not continue to lead them without interfering with their natural development and thereby breaking his creed of non-interference.  Soon after, Chronos Dracorum appointed 3 lieutenants to run the civilization.  These lieutenants strove in their own ways to lead the emits on in the same ways as Chonos Dracorum.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Lawful good.
\subsubsection{GOALS}
Argem -To obey the Time Dragon\\
Luilas - To find the person who can destroy the Destiny System.\\
Ergas ‚Äì To accurately record history for all eternity\\
\subsubsection{FOES}
They oppose the Sards.
\subsubsection{TEMPERAMENT}
They tend to be very even tempered,but will copy another temperament to fit in
\subsubsection{ATTITUDE ON LIFE}
They value life as sacred; however their life is not as important as the lives of those around them.
%\section{XAKAM}
%\subsection{BASIC INFORMATION}
%Elemental Alignment: Sky
%Class: Dark Race
%\subsection{PHYSIOLOGY}
%\subsubsection{GENDER} 
%Xakam have several distinct genders.Each Xakam can reproduce with any other Xakam of a different gender.
%\subsubsection{LIFE CYCLE}
%\subsubsection{HEIGHT AND WEIGHT}
%\subsubsection{ANATOMY}
%\subsection{SOCIOLOGY}
%\subsubsection{RELATIONS WITH OTHER RACES}
%\subsubsection{ECONOMY}
%\subsubsection{OCCUPATION}
%\subsubsection{LEISURE}
%\subsubsection{EDUCATION}
%\subsubsection{GOVERNANCE}
%\subsubsection{FAMILY}
%\subsubsection{HISTORY}
%\subsection{PSYCHOLOGY}
%\subsubsection{ALIGNMENT}
%\subsubsection{GOALS}
%\subsubsection{FOES}
%\subsubsection{TEMPERAMENT}
%\subsubsection{ATTITUDE ON LIFE}


\chapter{World Generation}
\begin{enumerate}
\item Before - The time before the world ended.  
%\begin{itemize}
%\item Development of Destiny System
%\item Creation of Sards
%\item Determined by previous future
%\end{itemize}
	\begin{enumerate}
	\item Empire - The glory of the people rise from the ashes
		\begin{enumerate}
		\item Dystopia - Cities fall to our darkest hour
		\item Crusade - War rages between corrupt leaders
		\item Guilds - Guild halls bring our greatest skill
		\item Expansion - Seeking a new home
		\end{enumerate}
	\item Gears - Science evolves the success of the people
		\begin{enumerate}
		\item Cyber - Evolving networks bring hope and ruin
		\item Steam - Wild frontier of steel and steam
		\item Arc - Ultra-Advanced technology in the blink of an eye
		\item Space - Boldly searching for a new home amongst the stars
		\end{enumerate}
	\item Magic - great houses lead the world with a new power
		\begin{enumerate}
		\item Monsters - From monsters of the past, civilization emerges
		\item Renaissance - Rebirth of lost skills and prosperity
		\item Science Fantasy - Using new powers to reach to the stars
		\item War - World wide war driven without end by Magic
		\end{enumerate}
	\item Ancients - Power of a forbidden time awaken
		\begin{enumerate}
		\item Crystal - Order and Chaos separated by the light of hope
		\item Dreams - Order destroyed in a land without physical law
		\item Horrors - When our nightmares roam the land
		\item Savage World - Everything gone; Only the strong remain
		\end{enumerate}
%	\item Drift
%		\begin{enumerate}
%		\item 
%		\item 
%		\item 
%		\item 
%		\end{enumerate}
	\end{enumerate}
\end{enumerate}

\appendix
\chapter{DEFINITIONS}
\section{KNOCKBACK}
At the end of an attack event,the target character is moved back namespaces in the direction of the attack.
\section{FLANKING}
Add a modifier for each attack preformed on the same hero in one round
+0 first attack\\
+3 second attack\\
+5 each subsequent attack\\
\section{ELEMENTAL BONUS}
+5 Super Effective\\
+3 Against Neutral\\
+0 No Effect\\
-5 Not Very Effective
\section{CRITICAL HITS}
Critical Hits are dealt every time a joker is drawn as the card bonus and at other times as determined by skills.  The effect of a critical hit is determined by the element of the weapon used for the attack.\\
\rowcolors{1}{white}{gray}
\begin{center}
\begin{tabularx}{\textwidth}{X X}
\hline
Affinity & Effect \\
\hline
No Element & + 5 modifier ignore skill buff caps for this attack \\
Law        & + 5 modifier ignore skill buff caps for this attack \\
Earth      & +1 damage on a successful hit \\
Sky        & Move 2 spaces after critical attack\\
Justice    & Buffs strength,speed,and Defense +2 for 3 turns\\
Sea        & Gain +1 skill for next action (lv5 -> $\Omega$ ->Tree $\Omega$) \\
Life & Heal 1 will on hit \\
Abandon & Ignore armor when calculating opponent's defense value\\
\hline
\end{tabularx}
\end{center}

\section{FOG OF WAR}
All characters see two spaces in fog of war conditions.  If a character cannot see a foe,they may not target them.  However,if an attack that targets a foe/object within sight would also hit a foe out of sight,both maybe hit.  
\section{BATTLE }
$Attack Value = (2 x strength)  + Weapon_{attack1} +Weapon_{attack2}+ specific_{skill1} + Specific_{skill2}  + card_{bonus}+ Attack_{Modifiers}$
$Attack_Modifiers = status_effects+ flanking + elemental_bonus$
$Defence Value = (2 x Defence)+ Armor_Stat+ Helm_Stat + Foot_stat+ Weapon_Defence+ Specific_Skill
+ Defence_Modifiers+5$
$Defence_Modifiers  =   status_effects$

Order of a Round
\begin{enumerate}
\item Resolve all status effects 
\item Draw cards for initiative add speed x2 for Initiative
\item Highest Initiative goes first in case of ties draw again for tie breaker
\item Continue in order of descending initiative
\item When last player has taken their first action; go back to highest initiative character; and if he or she has additional actions to take,then he or she may take them
\item Continue until all players have taken all actions
\item Decrease Durations of Status Effects by 1
\item If the durations of any status effects are 0 then remove them
\end{enumerate} 

 Order of Action
\begin{enumerate}
\item Check Range if in range continue; else stop
\item If Attack $>$ Defense then ability occurs; else ability fails
\item Reflex Interrupt; Knockback Occurs; Counter Occurs; Preflex Interrupt; Action is taken
\end{enumerate}

\section{NEUTRAL UNITS}
Span as a terrain feature; Treat as hero class character; randomly select a pair of Race and Action type
Race: see star journal for list of races
\subsection{Action Types}
\begin{itemize}
\item Aggressive: they always attack the closest units
\item Territorial: Attacks first thing with in a ring of spawn point
\item Peaceful: at first stand still but will attack last attackers if attacked
\item Wanderers: Move in a random direction each move
\end{itemize}
\subsection{ORDERS}
Actions for a computer controlled unit that may be assigned
\begin{itemize}
\item Order: basic action changes assignment of an allied unit that may take orders
\item Attack at will: attack nearest foe; will decide randomly if two are equally close; will use assigned ability
\item Attack Focus: attacks unit designated; when unit does not exists reverts to attack at will; will use assigned ability
\item Attack the Weak: target the enemy unit with the least HP; will prioritize the closest units first; randomly in a tie; will use assigned ability
\item Defend me: moves between the hero giving order and enemy forces: will use assigned ability if applicable
\item Defend Team: uses abilities to raise defense; will use assigned ability if applicable
\item Defend Lowest:  defends the friendly unit with the least HP; will prioritize the closest units first; randomly in a tie; will use assigned ability if applicable
\item Heal Me: heals unit who gives order; will use assigned ability 
\item Heal Team: Heals the nearest ally; will use assigned ability
\item Heal Lowest: Heals the ally with the least hp; will prioritize the \item closest units first; randomly in a tie; will use assigned ability
\end{itemize}
\section{SUPPLY/REINFORCEMENTS DROPS}
The item or troop that will be dropped is decided before battle.  They then are dropped when a character activates the drop ability.Supplies maybe any item and forces may be any hero.  The player calling the drop decides the target position.  Draw two cards for drift from this position.Royals cause no movement from target position.Spade numbers: move up one space; Heart numbers: move right one space; diamonds: move down one space; clubs: move left one space.Only one force
/ item may be dropped in one action even if more than one unit has objects to drop.  Only the character with the specific drop request may call the drop.
\section{TERRAIN}
\begin{itemize}
\item Neutral ‚Äì no effect
\item Encumbering- requires two movement actions to exit
\item Dangerous ‚Äì deal 1 damage
\item Defended -5 to defense modifier; cannot be seen in fog of war
\item Slick ‚Äì move two panels when exiting
\item Sky ‚Äì cannot be entered on without flight; if knocked back onto without flight skill then paralyze 1 and climb up
\item Relic ‚Äì allows magic/mechanics/ancients without exception; 
\end{itemize}
\section {CONDITIONS}
\begin{itemize}
\item Anti-Magic ‚Äì no magic skills may be used; spawn one relic
\item Anti-Mechanics ‚Äì no mechanics skills may be used; spawn one relic
\item Anti-Ancients ‚Äì no ancient skills may be used; spawn one relic
\item Fog of War ‚Äì see section on fog of war
\item Storm- randomly selects 1 sector to be attacked with highest attack value on board
\item High Energy- 15 MP available in the environment
\item Normal Energy ‚Äì 10 MP available in the environment
\item Low Energy ‚Äì 5 MP available in the environment
\item Neutral- no effects
\end{itemize}
\section{OBJECTIVE BASED FEATURES}
Depends on time period.  Can be interacted with using skills.May or may not have door; door may or may not be locked.
\section{IF THEN TRIGGERS}
This is the list of all possible triggers:
\begin{itemize}
\item Attacked ‚Äì triggers when the user is attacked
\item Long range ‚Äì triggers on the use of long range attack
\item Close combat ‚Äì triggers on use of a close combat attack
\item Special ‚Äì triggers on the use of magic/mechanics/ancients
\item Defense ‚Äì triggers on the use of defensive skills
\item Element- triggers on a specific element
\item Movement ‚Äì triggers when creature moves
\item Fence ‚Äì triggers when a creature moves inside radius of n panels
\end{itemize}

\section{EXPERIENCE POINTS AND LEVELING UP}
For each successful action and critical success (joker),one experience point is gained.  For every 30 experience points,1 level point is gained.  To advance a skill one level you must pay the amount of level points equal to the current level of the skill.
\section{CALL ALLY}
Call ally lv 1 the character does one ability\\
Call ally lv 2 the character does three abilities\\
\section{LAWS}
Any Trigger except fence may by the law that must be followed.  The following bonuses may be gained:
\begin{itemize}
\item +1 will
\item +1 strength
\item +1 defense
\item +1 Speed
\item +1 experience
\end{itemize}
\section{RESEARCH}
Items can be researched using the Technical Knowledge Skill.  Each unit of research requires 1 exp be expended.  The exp cannot be used to level up.  The following items can be researched\\
\begin{tabularx}{\textwidth}{l X r}
\hline
Item & Effect & Cost \\
\hline
Alloy & Material with a $6/6$ strength & 4 units \\
Harmonizer & Helm Allows access to Ancients skills & 12 units\\
Mechas & Helm Allows access to Mechanics skills & 12 units \\
Mystic Gem & Helm Allows access to Magic skills & 12 units\\
Power Suit & Armor that holds up to 5 Racial Skills beyond Cap & 24 units\\
Bionis & Armor that holds 1 skill that can be improved & 24 units\\
Data Density & Armor that holds 5 abilities& 24 units\\
Gene Splicer & Armor that holds a level one racial skill ignore cap & 24 units \\
Great Power & Armor that holds 5 MP & 24 units\\
\end{tabularx}
\section{GREAT ALCHEMY}
The following items can be produced using the great alchemy skill:\\
\begin{tabularx}{\textwidth}{l X}
\hline
Item & Effect\\
\hline
Golem& Creates a moveable unbreakable object \\
Gold & Worth the same as 1 unit of Processenium when traded\\
Philosophers Stone & Stone that holds 5mp but can be exchanged to revive a character without fail ignore all other restrictions.\\
\end{tabularx}\\

\section{SPECIAL CASTS}

\begin{tabularx}{\textwidth}{l X r}

\hline
Element & Effect & Difficulty \\
\hline
Abandon & Prevents KO from having an effect for 3 turns & 17 \\
  &Change condition to all prohibitive except user & 17\\
  & Target deals damage x2 but suffers ¬Ω damage as recoil & 19\\
  &Creates skill number characters from target character each with 1 different skill from target character & 19 \\
Earth & Create vines that move out at beginning of turn dealing 1 damage to targets in path & 17 \\
  & Prevent all damage and forbids move; Each time this is used successively manna burn deals turns +1 damage & 17 \\
  & Requires full HP.  If manna burn: user takes 1 damage. If no manna burn: target suffers User Will. +2 damage and User now has 0 Will. & 20\\
  & Target characters are now in double soul state for 3 turns & 19 \\
Justice & Target gains Move Type: Teleport for 3 turns & 17\\
  &Change condition to all permissive & 17\\
  &KO caster and revive all allies; Fails if manna burn& 20\\
  &Draw a card for each character (friend and foe) and KO all that receive a black card; Fails if manna burn & 20\\
Life & Heal 3 to target& 15\\
  & Deal 1 Damage and inflict Bleeding to target & 17\\
  &Revive target to 1 hp and prevent damage until targets next turn & 19\\
  &Clones targets character's equipment as a drone & 19\\
Sea & Weapons gain all attribute types for 3 turns & 15\\
  & Creates unbreakable block & 17 \\
  & Upgrade equipment by 1 level for 3 turns.  Refined alloy remains at boosted level & 19\\
  & Change all panels with in a ring 2 units wide to the same type of the casters choice & 19\\
Sky & Move target to any panel & 15\\
  & Move 3 and evade all counter attacks & 15\\
  & Chain lightning & 17\\
  & Allows Target character to take their action next & 19\\
Law & Randomly Inflicts 1 law for a chosen bonus & \\

\end{tabularx}
\section{RACIAL ABILITIES}
\begin{tabularx}{\textwidth}{l X}
\hline
Works Best With & Grants \\
Magic & $-2$ difficulty \\
  & +1 MP\\
  & Elemental Affinity $x2$\\
  & Magic does $+1$ damage against status afflicted characters \\
  & $+ 1$ duration for all Magic abilities \\
  & Access Magic Tree without Racial Specialty \\
Mechanics & 6th Skill that can be switched in and out using the Engine Skill \\
  & $+1$ Durability to Mechanics\\
  & Repair on after any successful action\\
  & Units adjacent to this hero cannot move away\\
  & Gain ability: build tower object with 3 will as action.  Mechanics abilities can be used while the tower is standing ignore durability\\
  & Access Mechanics Tree without Racial Specialty\\
Ancients & Ancients Durations $+1$\\
  & Cool down $-1$\\
  & Gain ability: Force target hero into cool down. \\
  & Use any ancient skill as the Skill modifier. \\
  & All ancient skills use a common pool.  Add duration to the pool when activating a new ability.  For each active ancients ability,subtract one duration each turn \\
  & Activate 2 ancients abilities in one turn \\
  & Access Ancients tree without racial specialty \\
Knowledge & 6th skill for knowledge skills \\
  & +1 to all heal intensities \\
  & Share knowledge skills with adjacent allies at $Lv-4$. \\
  & Prevent friendly fire\\
  & Boost 1 knowledge skill by 1 level\\
  & -3 difficulty for word spells \\
\end{tabularx}
\newpage
\begin{tabularx}{\textwidth}{l X}
\hline
Works Best With & Grants \\
Attack & Use long ranges skills without a long range weapon \\
  & Use the aim ability 3 time per battle without an action \\
  & Gain ability focus: inflict status that yields attack,defense,speed for 3 turns\\
  & Can use close combat abilities without a close combat weapon\\
  & +5 to all attack actions,-5 to all defense actions\\
  & Gain ability: prevent target hero from being revived.  Cannot be prevented if target hero has 0 will or less \\
Defense & May use 1 shield without using a hand equipment slot\\
  & + 5 to all defensive actions,-5 to all attack actions\\
  & If damage is >1 then damage -1 \\
  & Counters defend twice\\
  & -1 duration debuffs \\
  & Stealth duration +1\\
Racial &  Strength cap +2 \\
  &  Copy Racial ability \\
  & Will cap +2 \\
  & Speed cap +2 \\
  & Gain ability: Copy targets attributes\\
  & Defense cap +2\\
  & Access all $\Omega$ skills without using an additional skill slot.  Skill slots -1 \\
  & May use 1 attribute skill without using a skill slot\\
Vehicle & Characters using this vehicle may use skills\\
  & Equipment for vehicle may be exchanged with carried heroes\\
  & Capacity for 3 units \\
  & Move 2 spaces for each move action\\
  & Hands +4 \\
  & Ignore terrain,Hands -2\\
\end{tabularx}
\section{RACIAL SPECIALTIES}
\begin{tabularx}{\textwidth}{l X}
Specialty & Grants \\
Magic & Access Magic Skills\\
Ancients& Access Ancients Skills\\
Mechanics& Access Mechanics Skills\\
Vehicle& Access Vehicle Racial Abilities\\
\end{tabularx}

\section{FARMING}
Farming is accessed through the Naturalist Skill.  Creatures and plants in the farm are raised through solar units.  Each EXP the player earns is equivalent to 12 solar units.\\
\begin{tabularx}{\textwidth}{l X r}
\hline
Creature & Effect & Solar Units \\
\hline
Bitter Plant& Buff strength +1 for 10 turns ignore cap & 4\\
Sour Plant & Buff defense +1 for 10 turns ignore cap & 4\\
Salty Plant & Buff Speed +1 for 10 turns ignore cap & 4 \\
Sweet Plant & Buff will cap +1 for 10 turns ignore cap & 4\\
Spicy Plant & Modifier + 10 for 2 turns & 4\\
Fish & Buff defense + 5 and defense cap +2 for 3 turns & 12 \\
Milk & Increases buffs/debuffs durations by taking all countdowns on milk status for 3 turns & 6\\
Steak & Buff strength +5 and strength cap +2 for 3 turns & 12\\
Eggs & Decreases buff/debuff durations by making all count downs by 2 for 3 turns &6\\
Poultry &  Buff Speed + 5 and Speed cap +2 for 3 turns & 12 \\
Pork & Heal 5 will and will cap +2 for 3 turns &12 \\
Ore Golem & $Wood/Stone/Ore/Gem/Processenium$ & $12/24/36/48/60$ \\
Daycare & 1 exp for housed creature & 24\\
\end{tabularx}
‚ÄÉ

\section{REFERENCE TABLES AND GUIDES}
TO BE EXPANDED
\backmatter
\printindex
\end{document}

