\chapter{THE STAR JOURNAL}
\section{WHISPS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Life
Class: Light Race
Racial Area: Magic
Racial Specialty: can use all magic at -2 difficulty
\subsection{PHYSIOLOGY}
\subsubsection{GENDER}
The Whisps are androgynous.  They reproduce by budding.  Whisps bud every 10 a years on the summer solstice.
\subsubsection{LIFE CYCLE}
The average Whisps live for about 30 years with a standard deviation of 5 years.  As the Whisps age,their body temperature grows.  Whisps are considered to be young until their first budding.  Growth-wise,the Whisps are fully developed after the first year of life.  Development-wise,the Whisps are not fully matured until their first budding.  The gap between physical and mental development causes conflict because the youth are eager to act,but often do not have the sense of mind in order to act properly.  During the middle phase (from the 1st budding to the 2nd budding),the Whisps are at their physical prime.  During the last stage of life,the Whisps temperature slowly levels off.  When the Whisps die,their flame slowly fades until they die.
\subsubsection{HEIGHT AND WEIGHT}
The core of the Whisps body is a sphere that is 40cm in diameter.  As the Whisps age their trail ranges from 20cm to a meter in length.  The Whisps weigh about 20kg.
\subsubsection{ANATOMY}
The Whisps are constructed of plasma-like substance that is constructed in two main components.  The core is a sphere about 40cm in diameter.  The core is where most core functions of the Whisps take place.  The nervous, vascular, and digestive systems are located in the core.  The nervous system of the Whisps is remarkably developed to allow seamlessly interface with the Destiny system.  The Whisps use this system to as their primary means of locomotion as well as interacting with their physical environment.  This highly developed nervous system is also how the Whisps sense their environment.  Because the sensory system is not dependent on light, sound, or contact, the Whisps have extraordinary senses.  Their vascular system is an open vascular system with convection within the core being the primary means of circulation.  The digestive system produces energy by engulfing foreign objects and using chemical combustion reactions to extract the energy from the objects.  The other body structure is the trail.  It contains the reproductive organ where budding Whisps are developed.  The trail also contains a crystal encased nerve.  This nerve acts as an antenna for the central nervous system allowing the Whisps to extend their sphere of influence.  Other than the nerve in the trail, the Whisps do not have any internal structure.  The dermis of the Whisps is constructed of the same crystalline substance that coats the spine and is hot to the touch.  However, the dermis does not provide much protection from physical damage as the in depth integration with the destiny system is the primary method of defense.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Whisps tend to be peaceful towards other races.  This is mostly because while they can defend themselves,they can become easily overwhelmed due to their lack of physical defense inhibit and their 
\subsubsection{ECONOMY}
The Whisps use a market economy.  They specialize in enchanting materials produced by other groups.  The Whisps also use their superior intelligence to perform design and engineering work.  However,the high levels of intelligence and relatively fast reproductive cycle leads to an enormous highly qualified labor force that is competing for a comparatively small number of jobs.
\subsubsection{OCCUPATION}
The Whisps fulfill mostly tertiary sector jobs.  They specialize in engineering,energy,and product refinement.  Their engineers are some of the best of all of the races.  They focus on elegance in design.  Their work is considered to be exceptionally reliable and functional but not without cost.  The Whisps have a large energy sector.  They work to produce energy through Magic fueled energy systems.  The Whisps also work in product refinement.  Whips alchemists are considered to be highly skilled in their field.  
\subsubsection{LEISURE}
The Whisps have a large variety of leisure activities.  Many activities involve modifying games played by other races to require the use of magic.  For example,the Whisps play a ball game where the ball may only be struck with bolts of magic above a field where the players are flying around.  The Whisps also enjoy crafts and art.  One especially popular technique is to embed moving images into gems using magic.
\subsubsection{EDUCATION}
The Whisps educate their young by transmitting knowledge using magic through the antenna in the trail.  This allows huge and effective data throughput, but is exhausting for both the teacher and pupils.  Primary and Secondary education takes place in the first 3 years of life.  The Whisps School is often scheduled only once a month.  After the first 3 years the Whisps then are apprenticed for the next 5 years in a variety of different areas.  During this time, the Whisps will explore a variety of different career paths until they find one that they have great skill.  After a career path is chosen, the Whisps begin a two year long application process as they compete for positions in the best companies.  Then only the most talented are given jobs, the rest often emigrate to find work.
\subsubsection{GOVERNANCE}
The Whisps are governed by a Republic.  The laws ensure equality of opportunity for its citizens and provide a frame work to resolve disputes.  The laws are enforced by old magic powered by the life force of all Whisps.  The fact that the laws are enforced consistently across all Whisps and mediated by an exterior force prevents tampering and allows for an efficient and minimalist government.
\subsubsection{FAMILY}
The Whisps place moderate importance on the Family unit,but greater importance on the community.  This means while the Whisps respect and appreciate their parents from which they bud,The Whips place greater importance on the overall wellbeing of the society in which they live.
\subsubsection{HISTORY}
No one knows when or why the Whisps were created.  The oldest records that exist do not even include the formation of the Republic which happened in the early days of their race.  The Republic has ruled for many generations and likely will continue to rule.  Occasionally there are young Whisps who wish to dismantle the Republic by unraveling the wards that hold it in place; however, these efforts have been unsuccessful due to the fact the wards are tied to the lives the Whisps.  The Republic has successfully defended itself against invasions of opposing races including the Zar?ock and Navicos.  The Navicos invasion was short lived.  Some historians have argued that the invasion was actually aggressed by the Whisps and the Navicos were simply exploring.  Whisps would argue extensively that this is simply not true.  The Zar?ock continued their efforts for several generations before being successfully driven away.  These invasions left the Whisps strongly cautious of any actions by these two races.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Whisps generally follow a lawful alignment
\subsubsection{GOALS}
The goals of the Whisps are:
\begin{enumerate}
\item To continue their own existence
\item To enjoy life through self-perfection
\end{enumerate}
\subsubsection{FOES}
The Whips do not actively seek out foes; however,they have and do fight to defend themselves.  Their primary enemies include races that have the physical prowess to overtake them such as the Navicos and Zar ock.
\subsubsection{TEMPERAMENT}
The Whisps tend to have a short temper.
\subsubsection{ATTITUDE ON LIFE}
Whisps view life as a time to explore.  There is nothing before or after.
\section{NAVICOS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Sea
Class: Light Race
Racial Area: Magic
Racial Specialty: Strength +2
\subsection{PHYSIOLOGY}
\subsubsection{GENDER}
The Navicos are Male and Female.  The Males are slightly larger than the females.
\subsubsection{LIFE CYCLE}
The Navicos live on average 80 years with a standard deviation of 10 years.  The Navicos are raised by their family until age 10.  The Navicos are completely physically and mentally mature around age 20.
\subsubsection{HEIGHT AND WEIGHT}
The Navicos are on average 1.75 meters tall.  They weigh approximately 90 kg.
\subsubsection{ANATOMY}
The Navicos have two arms and two legs.  They walk primarily upon their two legs, but they can sprint using all four limbs. The Navicos are completely covered in blue fur with darker stripes.  This fur aids them in camouflaging themselves in the water.  Under the fur is a thick rubber-like skin that helps to seal in water.  The Navicos have superior vision and hearing facilitated by their larger eyes and ears.  The Navicos have claws that grow above their hands and feet.  They use these claws for a variety of purposes.  The toes of the Navicos are webbed to facilitate faster swimming. Compared to other races, the Navicos have considerable muscle mass. Internally, the Navicos are mostly unremarkable.  Their features are similar to humans with the exception of the respiratory system.  The Navicos have an additional pair of diaphragm muscles that can be used to quickly clear water from the lungs.  The respiratory system is also capable of processing larger amounts of oxygen and of filtering out carbon dioxide more efficiently.  This allows the Navicos to survive for extended periods of time under water.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
The Navicos are geological explorers by nature and natural drifters.  This has both helped and hindered their relations with other races.  One notable example occurred when a Navicos ship landed in Whips territory.  Seeing the action as an act of War,the Whisps attacked.  The willingness to not occupy territory has allowed the Navicos to form workable relationships with the Zar ock and Tessaran.
\subsubsection{ECONOMY}
The Navicos economy is primarily funded by trading with other races.  The Navicos are premiere navigators and ship builders.  They use these skills for a price for any race seeking transport.
\subsubsection{OCCUPATION}
Navicos earn their income by serving on ships.  Hence,they spend most if not all their life onboard ships.  These ships have a variety of roles ranging from cook,quartermaster,and captain.  The exact number and variety of roles depends on the ship.  However,one role is always filled: the Navigator.  The Navigator serves as an advisor to the captain.  It is the most respected role on a ship even more so than the captain.  The Navigator reminds the crew of their duties to the world around them and to their souls.  The Navigator encourages the crew to seek the Creator in all they do.
\subsubsection{LEISURE}
There is extensive time available on a ship on a long voyage.  As such the Navicos are constantly searching for ways to entertain themselves.  They enjoy mostly sports and shun the academic.  Young Navicos will compete in tests of strength.  
\subsubsection{EDUCATION}
The Navicos are educated in a teacher-apprentice manner.  This process is quite lengthy.  They learn what ever skills they need to complete their current role and little more.  However,they are typically adept at whatever they put their effort towards.  Over their lifetime a Navicos may have 3 teachers.
\subsubsection{GOVERNANCE}
The Navicos do not have a centralized governmental structure.  Instead each ship operates as an independent body.  There are 4 authority figures on every ship: the Captain, the Purser, the Quartermaster, and the Navigator.  The Captain has sole executive authority.  He decides what tasks the ship will pursue and how they will be pursued.  The Purser is the keeper of all funds.  He is responsible for paying all hands aboard ship and has the sole authority to remove the Captain from his post.  The Quartermaster Is the second in command of the ship and responsible for all cargo aboard ship.  The Navigator serves as an advisor.  The Navigators travel from ship to ship leading their ship.  They are exempt from the Captain?s authority but rely on the crew for their wellbeing.  The crew decides the pay of the Navigator at the end of the Voyage.
\subsubsection{FAMILY}
The family structure is important for the first 20 years of a Navicos s life.  After this time period,the Navicos leaves his family and he or she serves his or her Captain solely.
\subsubsection{HISTORY}
The Navicos are another very old race.  The most important element to the Navicos history is the history of the Navigators.  According to records,the ships of the Navicos once traveled without Navigators.  These early ships would often fight and dispute causing severe damage to all involved.  Eventually a group of young Navicos sought to end the violence.  They found an old book with faded gold lettering on the cover floating in the sea.  The Navigators were fascinated by its message and spread it to the crews.  The crews of these ships mutinied against their wicked captains,and the captains were relieved by the pursers.Since then the ships have been peaceful and a Navigator is always on board.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
The Navicos are Lawful and Good.
GOALS

\begin{enumerate}
\item Keep the commandments of the book of the Navigator
\item Obey the Captain
\item Fulfill the Charter
\end{enumerate}

\subsubsection{FOES}
The Navicos tend to be happy go lucky and do not have major enemies
\subsubsection{TEMPERAMENT}
The Navicos are easy going
\subsubsection{ATTITUDE ON LIFE}
Life is a sacred gift of the Creator


\section{TESSARN}
\subsection{BASIC INFORMATION}
Elemental Alignment: Electric
Class: Light Race
Racial Area: Mechanics
Racial Specialty: Can have up to 6 skills.  The 6th skill is stored and can be switched as an action.
\subsection{PHYSIOLOGY}
\subsubsection{GENDER}
Tessarn are hermaphroditic.  There must be at least two Tessarn for procreation
to occur.  
\subsubsection{LIFE CYCLE}
The Tessarn have two life cycles that occur concurrently.  First the physical
life cycle occurs over a period of 5 years.  Second the psychological life span
takes place over a period of on average 100 years with a standard deviation of
10 years.  While the physical body will die, the psychological conscious will
be transferred to the next body at the time of physical death.  The twin nature
of their life cycle is important for several reasons.  Firstly, the Tessarn can
change their physical appearance to adapt to the environment around them.  For
example, if the Tessarn enter an environment with large quantities of water it
can adapt its form to include flippers and other adaptations that allow it to
thrive in its new environment.  Secondly, because the psychological conscious
does not change with the physical body, it allows the Tessarn to learn from the
past experiences from each iteration of its physical form and not has to
relearn information between after iteration.    
\subsubsection{HEIGHT AND WEIGHT}
Tessarn dimensions vary greatly.  They typically range from .5 meters tall to
as tall as 2.5 meters tall.  Their weights range from 5kg to 200kg.
\subsubsection{ANATOMY}
The Tessarns have an extremely veritable anatomy.  There are some common
components.  First there is a core.  The core is cylindrical in appearance and
houses the psychological conscious of the Tessarn, its memory, and the genetic
information of the physical form of the Tessarn.  The memory and genetic
information are stored as digital information within the Tessarn.  Ports on the
base of the cylinder are the means of data transfer between two Tessarn that
allow for data transfer and reproduction.  The physical body changes every 5
years and rarely stays constant.  It is typically constructed from organic
materials using advanced chemical processes; however, in extreme climate
situations, the Tessarn can produce a non-organic physical form.  The changes
are often drastic and allow the Tessarn to quickly adapt to the environment
around them.   Even the digestive and respiratory systems can completely
change.  A Tessarn can be a Carnivore before iteration and an Herbivore after
the iteration.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
As a whole,the Tessarans will quickly change their relationships in order to
maximize their current situation.  For example if an associate suddenly becomes
unpopular,it is not uncommon for it to be abandoned.  If someone becomes
popular the Tessarn will quickly begin to wheel and deal to become in that
individual s good graces.  This has earned the Tessarn a reputation as
untrustworthy amongst most races.
\subsubsection{ECONOMY}
The Tessarns will quickly change their economy and mode of economy to adjust to
their current environment to maximize their profits.  In situations where a
socialist economy is most effective for the whole it will be employed.  In
situations where a market economy is most effective it will be used.  Tessarns
tend to be short sighted in their planning making the best use of what works
now in order to be successful.  The changes in their economy tend to line up
with their 5 year iteration cycle.
\subsubsection{OCCUPATION}
Tessarn are extremely well adaptable to any job they are put to.  The Tessarn
will optimize themselves to complete the tasks they need to complete when they
physically iterate every 5 years.  Outside of their specialty,the Tessarn tend
to be mostly useless.  They are generally gifted with the area of technology
but even this can be rotated out of their abilities to make room for other
abilities as the need arises.
\subsubsection{LEISURE}
Leisure is seen as a waste of time and resources.  The Tessarn are strictly
functionalist.
\subsubsection{EDUCATION}
Tessarn use the same data transfer protocols used to transfer their genetic
information to transfer to other Tessarn.  Any further education is seen as a
waste of time and energy.
\subsubsection{GOVERNANCE}
The Tessarn view governance as a waste of time and energy.  The only law that
governs them is the survival of the fittest.
\subsubsection{FAMILY}
Time spent raising offspring is seen as a waste of time and energy.   There is
not a family structure.  
\subsubsection{HISTORY}
The Tessarn arose from an artificially intelligent robotics experiment.  As the
time passed the Tessarn began to be completely autonomous.  Eventually the
Tessarn developed organic computing and their modern form developed.  There are
some Tessarn that object the short-termism of the Tessarn as a whole.  These
Tessarn tend to be more successful in the long run however are often criticized
for not be as adaptable as the other members of their race.  These individuals
are highly respected by other races for their actions but tend to not receive
the same respect at home.  Over time the majority of Tessarn have attempted to
phase out the more long-term orientated Tessarn but have been unsuccessful not
seeing an incentive for anything more than a passive effort to eliminate them.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Lawful
\subsubsection{GOALS}
To achieve optimal performance.
\subsubsection{FOES}
The Tessaran have no distinct foes but they also do not have any distinct
allies either.
\subsubsection{TEMPERAMENT}
Tessarn have whatever temperament best suits the situation they are in.  Logic
is valued and Emotional action as a whole is seen as inefficacy.
\subsubsection{ATTITUDE ON LIFE}
Life exists to produce a better next generation.
\section{ZAR'€™OCK}
\subsection{BASIC INFORMATION}
Elemental Alignment: Earth
Class: Light Race
Racial Area: Magic
Racial Specialty:  Can use long range attacks without a long range weapon
\subsection{PHYSIOLOGY}
\subsubsection{GENDER} 
Zar ock are male and female.  They reproduce by the female laying eggs that
develop in the nest.
\subsubsection{LIFE CYCLE}
The Zar?ock life cycle begins at the egg.  The eggs grow in nests of hundreds
of eggs.  After about 6 months in the eggs, the larval form will emerge.  The
newly hatched larvae are extremely hungry.  They will eat the first thing they
see; even if the first thing they see is one of their fellow hatchlings.  After
a few hours around a hundred larvae remain.  These Larvae quickly learn to
survive.  They are born with an innate battle instinct.  After assuring a
source of food, the Zar?ock will begin to form a web and fashion tools.  This
stage will continue for several years.  After about 30 years the Zar?ock will
mature.  At this time, they will have developed a large web and sizable arsenal
of weapons.  Some Larvae will go through a metamorphosis.  The metamorphosis
process takes only a few hours.  After metamorphosing, the Zar?ock emerges
fully developed and matured with large wings and are overall far more
dangerous.  Only Zar?ock that metamorphose are capable of reproducing.  At
about 50 years of age the Zar?ock dies.  When they die they are often used to
feed the next generation.
\subsubsection{HEIGHT AND WEIGHT}
Zar ock are 3 meters tall in the larval stage and 5 meters tall in their
metamorphosed state.  They weigh 1800 kg and 3600 kg respectively.
\subsubsection{ANATOMY}
The anatomy of the Zar?ock differs on two factors: state of life, and sub
species.  Within each state of life there are only slight differences between
subspecies.  The larval stage has 10 limbs: 8 legs and 2 arms.  The body stands
erect on all eight legs and uses the arms to perform a variety of tasks ranging
from devouring foes to wielding weapons.  The adult stage has 16 limbs 8 legs,
4 arms, and 4 wings.  Both types have the same type exoskeleton.  The
exoskeleton makes them incredibly strong.  They have 8 eyes arranged on the
head portion of the exoskeleton.  These eyes allow the Zar?ock to see almost
all the way around themselves without turning their head.  Only 30 degrees
directly behind the head is not visible.  Internally, the Zar?ock have an
unremarkable digestive, open circulatory system, and respiratory system.  The
digestive system has a distinct feature.  In addition to its normal function,
the digestive system will allow the Zar?ock to process their food into web.
The web is remarkably strong.  The Zar?ock use this web both to secure pray but
also as their primary building material.  The Zar?ock are mildly intelligent
and are capable of communication and problem solving. The Adult form has the
same features except it grows an additional pair of arms and 2 sets of wings.
These wings are used to transport the Zar?ock short to medium distances in
pursuit of their prey.  There are 6 distinct subspecies.  Each subspecies can
be identified by the unique coloring of their exoskeleton.  Reds have slightly
stronger arms and thicker exoskeletons.  They primarily serve as guards for the
web.  Blues have superior eyesight and fine motor skills.  They are capable of
wielding bows with ease.  They serve as snipers taking out foes with the bows
and web.  Yellows are the fastest.  They have the ability to paralyze their foe
with a venomous bite.  Greens have the thickest exoskeleton and are the most
intelligent.  Their increased intelligence gives them an aptitude for magic.
Whites are rarer and are the queens of the web.  They have the strongest web.
They have additional glands that secrete powerful hormones that can both seduce
prey and call hordes of Zar?ock to their aid.  Blacks are the Kings by far the
rarest.  They have the all of the preceding characteristics plus an
unquenchable blood thirst.  Even other Zar?ock tends not to like King Zar?ock.
    One would be remiss to avoid taking about the importance of the web to the
    anatomy of and function of the Zar ock.  It functions almost as an
    extension to the Zar ock that it houses.  The Webs are enormous cavernous
    structures.  Zar ock store food,lay eggs and preform most of their lives
    within the walls of the web.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Zar ock have poor relations with other races.  Only Greens even consider the
regularly consider the possibility of working with other races.  These
relations are often tempered with the knowledge that the Zar ock are known to
eat those they don t like.
\subsubsection{ECONOMY}
All actions with in a web are centered on the Queen and possibly King of the
Web.  They will likely request items be built to suit their needs or to fulfill
needs within their webs.  For example tools could be build that are then
rationed out to the others in order to defend the web or build a large object.
\subsubsection{OCCUPATION}
The Zar ock often work in serve of their king or queen.  Whatever he or she
asks them to do they often will do it.  Outside of the webs of kings and
queens,the Zar ock are skilled mercenaries and smiths.  The Greens are even
moderately skilled mages.
\subsubsection{LEISURE}
The Kings and Queens will often laze about doing whatever pleases them.  They
enjoy mostly carnal pleasures such as gorging themselves on food or torturing
their underlings in a variety of ways.  Occasionally a King will lead its
forces into battle; however,this is uncommon albeit terrifying experience.  In
free webs,the Zar ock will mostly play sports and occasionally study culture
and history.
\subsubsection{EDUCATION}
Zar ock are not educated.  If they die as a result they are viewed as not worth
the effort anyway.  Very seldom,a queen or a green will learn to read and study
cultures of other races but this is uncommon even in the free webs.
\subsubsection{GOVERNANCE}
The queen strongly influences the actions of the other Zar ock through her
hormones.  To them,her secretions are a highly addictive drug.  Zar ock that
are exposed will experience an unimaginable high but will also go through
severe withdrawal just hours later even after one exposure.  To this end the
queens will withhold this addicting serum in order to get what they want.
Often Queens will never work and will have their slaves construct huge webs for
them.  Kings behave in much the same way except they often work to steal and
kill for their spoils.  In free webs,the Zar ock are ruled by a total
democracy.  As there are relatively few of them,this works well.
\subsubsection{FAMILY}
Zar ock have no family aside from the unshakable loyalty to their King or
Queen.  In the free webs,Zar ock treat the entire community as extended family
with their specific subspecies as family.  The oldest female is considered the
leader of this family.
\subsubsection{HISTORY}
The Zar?ock are a very old race.  They have existed since the beginning of
creation much to the detriment of other societies.  After several generations,
the first queens were born.  They used their chemical charm to build large
webs.  Despite the oppression their underlings endured, The Zar?ock flourished
during this time and many of their now greatest skills were developed.  After
several millennia, a King was born.  The king started a great war against the
other races.  This war led to the Zar?ock taking over large territories.  After
the king passed, the other races reclaimed much of their lost lands.  In the
few Kings who have lived since, each has attempted to reclaim the glory of the
first King.  This also led to the creation of several distinct hordes of
Zar?ock as the races were often unable to completely remove the Zar?ock from
their previous territory.  Eventually a small group of Greens and other Zar?ock
were able to escape addiction.  They formed their own democratic web.  Without
the addictive hormones to ensure cooperation, their web has faced many
problems, but their civilization is the most developed of any Zar?ock horde.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Kings,Queens,and Others: Evil
Free Webs: Neutral
\subsubsection{GOALS}
Queens and Kings: To have the most property than any Zar ock ever
Others: To serve the King or Queen.
Free Webs: to live life to the fullest
\subsubsection{FOES}
Almost all races hate the Zar ock.  Few races will even agree to live near free
web Zar ock for fear of attack.
\subsubsection{TEMPERAMENT}
Zar ock have horrible tempers.
\subsubsection{ATTITUDE ON LIFE}
Life here and now is all there is.
\section{DRAS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Earth
Class: Light Race
Racial Area: Ancients
Racial Specialty: Can access Mechanics Abilities
\subsection{PHYSIOLOGY}
\subsubsection{GENDER }
The Dras are androgynous.They reproduce by budding from the body of a dying
Dras.  Dras usually only produce one offspring; however,the older the Dras the
more offspring it will produce upon its death.
\subsubsection{LIFE CYCLE}
The average Dras lives for about 10,000 years with a standard deviation of 1000
years.  Because of their long lifespan they measure their age in centuries.
They refer to centuries as cycles.  Each cycle is divided into 100 clicks.
Dras are considered to be young from birth to about 20 cycles.  During this
time, Dras are relatively weak and if killed during this time period, are
unable to reproduce.  As a Dras approaches its 20th cycle, it will go through a
stage where it becomes able to bud offspring.  This process is very painful for
the Dras.  It will experience great growth.  The growth of a Dras consists of
the development of its muscles and its mind to its adult stage.  Until a Dras
reaches this point in its development, it is only capable of feeding and
listening.  It is otherwise unable to act.  However after its metamorphosis, it
gains great strength, stamina, and ability.  A Dras will continue to experience
minor growth and development until its 80th cycle.  At that point in its life
cycle, it will halt development.  Dras that live to beyond their 100th cycle
begin a second metamorphosis.  Unfortunately, many Dras die during this
process; hence, the average life span of 10,000 years.  After the second
metamorphosis, the upper limits on a Dras's power disappear.
\subsection{HEIGHT AND WEIGHT}
Dras are on average 1.5 meters tall and weigh about 150 kg.
\subsubsection{ANATOMY}
Their anatomy is humanoid except they have 4 arms and 2 legs.  Their skin is a
hard exoskeleton that serves as a heat-sync, photo voltaic cell, and an oxygen
scrubber.  The exoskeleton is very dense but has blood vessels in complicated
networks just below the surface to cool blood and assist with the energy
production process. Under the exoskeleton, Dras has several body systems. They
have a vascular circulatory system except it contains several smaller ?hearts?
located at the periphery of the chest cavity that assist the primary heart
located in the abdomen at pumping blood around their bodies.  Their respiratory
system is located in their exoskeleton tiny pores located allow over the Dras
allow gas to enter and then be processed by powerful cleaning cells.  The Dras
do not have a digestive system; instead, their exoskeleton contains photo
voltaic and photo chemical cells that produce chemical and electrical energy
directly for use by the body.  The Nervous system of the Dras is distributed
across the entire organism; however a core located in the midsection of the
organism processes sensory information and processes goal oriented behavior.
The Dras use the differing light quantities coming into their bodies to
determine visual surroundings, and a similar process is used to determine
sound.  The Dras have a high powered energy core in their chest.  This is where
unneeded energy is stored, and where after the 1st metamorphosis, atomic fusion
is used to produce the chemicals needed to sustain the Dras's life.  Until the
1st metamorphosis, the Dras lives off a reserve from its predecessor.  The
immune system of the Dras is also very potent.  All foreign particles are
passed to the energy core and decomposed into new particles eliminating any
threat of infection.  After the 1st metamorphosis, an organ develops that
begins to create the Dras that will bud from the current Dras after its death.
After the second metamorphosis, the Dras lose their hard exoskeleton.  The Dras
that survive use the fusion source in their chest to develop a new exoskeleton.
This process exposes the Dras to infection and other life-ending effects;
hence, many do not survive.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Dras are fiercely independent.  They will not interfere with other races.
\subsubsection{ECONOMY}
The Dras have little need for economy because they can synthesize anything they
need.  However,if it must it can make a bargain with another Dras or another
creature; they will exchange pieces of their fusion sparks.
\subsubsection{OCCUPATION}
Dras do not have formal occupations because they do not have an economy.
\subsubsection{LEISURE}
Dras do whatever they determine is best for them.
\subsubsection{EDUCATION}
Dras are fiercely curious.  Dras observe the world around them to learn.  They
have near perfect memory and have no need of a formal education system.
\subsubsection{FAMILY}
Dras have no family because unless its parent Dras survives its second
metamorphosis,it will not have any living family.  Dras that are born as twins
will never separate willingly.  They behave more as one organism with two
bodies than two separate organisms.
\subsubsection{GOVERNANCE}
The Dras are governed by a council of 5 twice ascended Dras.  They are not
governed in the general sense of the word.  The council is more of an advisory
body.  The councils make decisions; however, each Dras is capable to disregard
the decisions of the council at will.  This disregard is a rare occurrence but
can happen.  Four of the members of the council represent the four cardinal
elements.  The final member of the council name is Dracorum Chronos.  He acts
as the leader of the council.  He is a powerful time mage and the only mage
ever to master complete control of time travel. The Dras Council is notorious
for its deliberate action.  No action is ever taken without extensive thought
and discussion.  In order for a decision to be made all five must agree.  
\subsubsection{HISTORY}
Dras have existed since before the time before.  They are remains of an old
prototype of the Destiny System that appeared to have failed.  They were
discarded by the scientists as failed experiments.  However, during the process
of disposal, they suddenly gained consciousness.  The Dras do not view the
scientists who made them as their creators.  They believe that even though the
scientists may have assisted in their awakening, it is far beyond their ability
to create the marvels of the Universe.  They instead search all of time and
space in order that they may find what they believe to the one true Creator.
Since their awakening, the Dras have lived alone in any part of the multi-verse
they can find.  They observed the other races to learn their skills and
abilities however never interfere with their subjects.  The Dras feel that
naturalistic observation is the only method that produces reliable results.
After several generations of Dras, There were 5 Dras who had survived the
second metamorphosis named: Chronos Dracorum, Prometheus, Gilgamesh, Thundolom,
and Gaius.  Each specializes in their own elemental abilities: justice, life,
sea, sky, and earth respectfully.  Each also focuses their studies on a
specific area of the multi-verse.  Chronos Dracorum being the oldest, wisest,
and most deliberate by far of his kind watches the development of civilizations
throughout all of time.  Prometheus the youngest takes personal interest in the
lives and interactions of different beings.  Gilgamesh the creative watches the
majesty and beauty of the sea.  Thundolom the knowledgeable takes sentinel over
the sky and space?s great mysteries.  Gaius the solemn often remains even more
alone than his fellows as he watches over the vast expanses of land in the
wilderness.  These Dras decided it was best for them to form a council to
protect each other and their kind.  While each of these five Dras is rarely
together, they will meet to defend their own and to prevent any catastrophe
that could endanger Dras kind or life in general.  They have never worked with
other races and many other races even deny the Dras exist.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Dras are Lawful Neutral and Non-Interventionist.
\subsubsection{GOALS}
Dras have three goals
\begin{enumerate}
\item To peruse knowledge of all forms through nonintervention to find and know the Creator
\item To prevent the destruction of the life of others to the extent that it does interfere with the first goal
\item To protect themselves only to the extent that it does not interfere with the first two goals
\end{enumerate}
\subsubsection{FOES}
The Dras Council is sworn enemies of the Sards who the Dras view as inferior
copies.  They despise the constant intervention of the Sards into life that
interrupts their naturalistic observation.
\subsubsection{TEMPERAMENT}
The Dras have an even temperament that comes from cycles of living
\subsubsection{ATTITUDE ON LIFE}
Life is the most valuable gift of the Creator
\section{EMITS}
\subsection{BASIC INFORMATION}
Elemental Alignment: Sea
Class: Light Race
Racial Area: Ancients
Racial Specialty: Can copy another race s specialty
\subsection{PHYSIOLOGY}
\subsubsection{GENDER }
Male and Female:  Those who drown while attempting to cross the waters of time
are reborn as Emits.  They lose their own memory in the process.  Despite the
existence of two genders they cannot reproduce.
\subsubsection{LIFE CYCLE}
Emits are immortal creatures,but they can be killed by sustaining fatal damage.
They only have an adult stage; however,their apparent age is directly tied to
the time period they currently occupy.  In the time of before,they appear as
infant child of the race they are currently imitating.  In the time of the
past,they appear as young children of the race they are currently imitating.
In the middle ages,they appear as adolescents of the race they are currently
imitating.  In the present,they appear as adults of the race they are currently
imitating.  In the future they appear as elders of the race they are currently
imitating.  
\subsubsection{HEIGHT AND WEIGHT}
Emits copy the height of the race they are currently imitating.  Emits weigh
about 50 kg despite the form they currently hold
\subsubsection{ANATOMY}
Their anatomy changes to match the race they are currently intimating.  While
alone or with only other Emits,they appear as white formless humanoids.
\subsection{SOCIOLOGY}
\subsubsection{RELATIONS WITH OTHER RACES}
Because Emits copy the appearance of other races when they are around them,they
have no specific racial agreements or disagreements.
\subsubsection{ECONOMY}
They copy the economy of the race they are living with.  When alone,they will
barter if necessary.
\subsubsection{OCCUPATION}
They copy the occupation of the race they are living with.  When alone,they
will specialize in a specific task they have done before.  Often,they fill
government positions or serve in the tertiary job positions.  One group of
Emits tasks themselves with the task of restoring time to its normal flow as
well as preventing blockages of its flow.  Another group writes a text known as
the Star Journal that is a record of all life in the multi-verse.  This group
is very stoic in its efforts to ensure that nothing is missed.  It is
considered an honor to be a member of this group.
\subsubsection{LEISURE}
They copy the leisure of the race they are living with.  When alone,they will
spend time swimming and participating in other aquatic activities.  Emits will
often spend extensive periods of time reflecting the events of the day and the
actions of others.
\subsubsection{EDUCATION}
They have vast knowledge from the water of time and see no need for formal
education.  However,they will participate in the educational systems of other
races both as teachers and students in order to fit in as necessary.
\subsubsection{GOVERNANCE}
The Emits operate under a dictatorship.  The dictator is a very old creature
known as the Chronos Dracorum.  It is a living embodiment of time.  Under the
Chronos Dracorum, there are 3 lieutenants: Ergas, Luilas, and Argem.  Each
supervises an aspect of emit life.  Ergas is the Great Historian.  He keeps is
responsible for all of the records contained in the Star Journal.  He and his
followers work to record detail accounts of history.  Luilas is the Great
Guardian.  He is the enforcement arm of the Emits.  His followers work to
protect as many beings as possible by actively interfering with time.  He and
his followers were banished from the fountain of time for their actions by the
Chronos Dracorum and Argem, but some Emits are sympathetic to his cause.  Argem
is the Great Rememberancer.  He and his followers work to ensure that the
Chronos Dracorum?s will is carried out in his absence.  He often opposes the
actions Luilas and occasionally Ergas for their interference in time.
\subsubsection{FAMILY}
They copy the family life of the race they are living with.  Emits have no
families on their own.  They live as a huge single-family units.
\subsubsection{HISTORY}
They exist from the flow of time.  The Emits follow a twice metamorphosed Dras
known as Chronos Dracorum.  This Dras was a master of time magic and uses the
form of a large dragon as its exoskeleton.  The Emits are the result of his
fusion-spark interacting with the time stream.  Chronos Dracorum created the
Emits to assistant him in his mission to observe the universe.  The Emits
prospered under the rule of Chronos Dracorum benefitting from his vast
knowledge and leadership.  Chronos Dracorum realized that the Emits were
becoming more and more sentient.  He felt that he could not continue to lead
them without interfering with their natural development and thereby breaking
his creed of non-interference.  Soon after, Chronos Dracorum appointed 3
lieutenants to run the civilization.  These lieutenants strove in their own
ways to lead the emits on in the same ways as Chonos Dracorum.
\subsection{PSYCHOLOGY}
\subsubsection{ALIGNMENT}
Lawful good.
\subsubsection{GOALS}
Argem -To obey the Time Dragon\\
Luilas - To find the person who can destroy the Destiny System.\\
Ergas - To accurately record history for all eternity\\
\subsubsection{FOES}
They oppose the Sards.
\subsubsection{TEMPERAMENT}
They tend to be very even tempered,but will copy another temperament to fit in
\subsubsection{ATTITUDE ON LIFE}
They value life as sacred; however their life is not as important as the lives
of those around them.
%\section{XAKAM}
%\subsection{BASIC INFORMATION}
%Elemental Alignment: Sky
%Class: Dark Race
%\subsection{PHYSIOLOGY}
%\subsubsection{GENDER} 
%Xakam have several distinct genders.Each Xakam can reproduce with any other Xakam of a different gender.
%\subsubsection{LIFE CYCLE}
%\subsubsection{HEIGHT AND WEIGHT}
%\subsubsection{ANATOMY}
%\subsection{SOCIOLOGY}
%\subsubsection{RELATIONS WITH OTHER RACES}
%\subsubsection{ECONOMY}
%\subsubsection{OCCUPATION}
%\subsubsection{LEISURE}
%\subsubsection{EDUCATION}
%\subsubsection{GOVERNANCE}
%\subsubsection{FAMILY}
%\subsubsection{HISTORY}
%\subsection{PSYCHOLOGY}
%\subsubsection{ALIGNMENT}
%\subsubsection{GOALS}
%\subsubsection{FOES}
%\subsubsection{TEMPERAMENT}
%\subsubsection{ATTITUDE ON LIFE}

